### 2014-05-15 doc/paper/paper.tex
Added everything from old iser repo

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}

\begin{document}

\mainmatter

\title{Autonomous Realization of Simple Machines}
\author{Can Erdogan \and Mike Stilman}
\institute{Institute for Robotics and Intelligent Machines \\Georgia Institute of Technology}

\maketitle

\begin{abstract}

For robots to become integral parts of human daily experi- ence, they need to be able to utilize the
objects in their environment to accomplish any range of tasks. In this work, we focus particularly
on physically challenging tasks that push the limits on the robot kinodynamic constraints such as
joint limits, joint torques and etc. Previously, we demonstrated an autonomous planner that
instructs a human collab- orator where to place the available objects in the environment to form a
simple machine such as a lever-fulcrum assembly. In this work, we report results on the autonomous
realization of such a design by the humanoid robot Golem Krang, focusing on the challenges of
autonomous perception, manipulation and control.

\end{abstract}

\section{Introduction}

The ability to use the available objects in the environment towards accomplishing goals is essential
to thriving in challenging circumstances. Everyday examples of tool use include simple machines such
as levers and pulleys. The challenge in autonomous design of such simple machines is the space of
discrete choices for the component options and the related high-dimensional continuous configuration
space of the chosen components.

In previous work \cite{erdogan2013planning} \cite{erdogan2014incorporating}, we demonstrated the
constraint satisfaction approach to assembly design, specifically for robotic manipulation and
locomotion. The key idea is to represent the constraints
between the components of the design, the robot kinematics and dynamics as generic equality and
inequality functions within a nonlinear optimization framework and solve for the global minima, if
necessary by random restarts. Such global optimization methods have been used in other fields as
well, such as operations research \cite{vidal2006branching} and architecture \cite{yu2011make}.

In this work, we take the next step towards full autonomy where the humanoid robot, Golem Krang,
autonomously manipulates the objects in its environment to construct a simple machine. We present
an autonomous planner that perceives the available objects, specifically 15 kg cinder blocks and 10
kg 2-by-4 block blocks (e.g. potential levers), relocates them to the desired configurations output
by the constraint planner, and actuates them to flip a 45 kg load. Figure \ref{fig:showOff} demonstrates key scenes
from this scenario such as (a) detection of a cinder block, (b) locomotion with a heavy load, (c)
manipulating a lever while subject to multiple constraints and (d) application of force to the lever
leading to a successful load motion.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/showOff.png}
  \caption{The mechanical advantage in forces}
  \label{fig:showOff}
\end{figure}

Significant effort has been demonstrated by \cite{beetz2010cram} \cite{stilman2005navigation}
\cite{kemp2007challenges} to incorporate autonomous agents in human environments. Our work stands
out in multiple aspects from the established state of the art. First, Golem Krang is a two-wheeled
balancing robot, similar to a segway with two 7-dof robotic arms installed. The challenge with
such a platform is the dynamic stability constraint where the robot has to ensure its center of mass
is close to the wheel axis at all times as opposed to legged or multi-wheeled platforms. Secondly, to the best of our knowledge,
Golem Krang is the tallest and heaviest two-wheeled robot with 150 kg at 1.9 m, a unique property
among similar designs \cite{kuindersma2009dexterous}. As we expand in Section IV, at this scale, the
weight can help with heavy-duty manipulation but complicates the autonomous locomotion of the
agent. Lastly, Golem Krang perceives its environment with an onboard RGBD sensor with two degrees
of freedom that are manipulated autonomously for gaze control. Autonomous perception and scene
recognition has only recently started to gather interest in the humanoid robotics field
\cite{srinivasa2010herb} \cite{nishiwaki2000design} as opposed to the long established motion
capture methods \cite{dasgupta1999making}.

\section{Technical Approach}

We now present our approach to autonomous construction of simple machines, particularly a
lever-fulcrum assembly to overturn heavy obstacles, in four major categories: (1) autonomous design,
(2) visual perception, (3) posture control, and (4) motion planning.

In any design, components have to be placed to satisfy a set of physical or domain constraints. For
instance, a candidate 2-by-4 block needs to make contact both with the load and the fulcrum,
essentially distance functions between objects, to satisfy physical constraints of the design.
However, for a design to be useful, we also impose that the contact point for the lever is further
away from the fulcrum than the load such that a mechanical advantage is achieved. In previous work,
we propose a nonlinear optimization approach where such geometric and dynamic constraints are
expressed as equality and inequality functions whose common zero-crossings are design configurations
that satisfy all the constraints. For this work, we use the planner to output the lever and the
fulcrum configurations, and the required contact point, but allow the robot to choose its closest
configuration, assuming it can supply the necessary force.

In perceiving the environment, we propose using a light-weight feature-based recognition approach as
opposed to full 3D based approaches that use the entire mesh data such as the iterative closest
point algorithm or over-segmentation methods. The key assumption of the work is that the planner
already knows the mesh of the available objects and with minimal additional feature knowledge, such
as the top of a cinder block is at 44 cm from the ground or a lever is at least 2 meters in one
dimension, we can speed up detection. At its current stage, the agent can autonomously detect cinder
blocks, the load as shown in Figure 1, the walls and the 2-by-4 levers. To localize objects of
interest, we perform a simple scan with the tilt and pan degrees of freedom of the RGBD camera,
taking also into account the robot kinematics. Figure \ref{fig:detection} demonstrates the detection module.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/detection.png}
  \caption{The mechanical advantage in forces}
  \label{fig:detection}
\end{figure}

For the locomotion controllers, we model Krang as a simple inverse pendulum and use a
proportional-derivative control with gain scheduling for different robot poses to minimize the
frequency of oscillations in dynamic balancing. In picking up cinder blocks, the torque around the
wheel axis due to the additional force at the end-effector is incorporated in computing the goal
balancing angle.

Lastly, for motion planning, we use a variety of approaches. First, to grasp objects, we use
analytical inverse kinematics to determine if there is a configuration close to the object we can
reach without collisions. Once close, we perform Jacobian inverse kinematics to approach the object
and detect contact with the object with the gripper force-torque sensor. Analytical inverse
kinematics is used as a resolution-complete method to determine whether a collision-free grasp
configuration exists as opposed to sampling the large configuration space of the arms to avoid local
minima with Jacobians. In addition to motion planning for the arms, we also make use of an example
of conformant planning in picking up a lever. The motivation is to avoid perception problems by
running each wheel to the 2-by-4 on the ground while the wheels cannot exert the torque to climb
over the object. Thus, the robot autonomously aligns itself with the object of interest by using
contact points without the need for precise perception.

\section{Results}

Our results demonstrate Golem Krang autonomously construct a simple machine design, specifically a
lever-fulcrum assembly, and use it to overturn a 45 kg load. To achieve such an autonomous behavior,
we propose a set of modules that accomplish object detection and localization, balancing and
navigation controller in the presence of external disturbances, and a rich set of motion planning
modules. To demonstrate the execution of the task, we designed the following scenario (see
\url{http://tinyurl.com/mw2ehxl} for video):

We position Golem Krang in the middle of the room and instruct it to use the closest cinder block as
a fulcrum. Using the aforementioned tools, the robot picks up the object (e.g. reacts to its weight
by leaning backwards) and carries it to the predetermined position instructed by the constraint
optimization planner. During locomotion, we assume that there are no obstacles on the path of the
robot, and the robot uses the turn-forward-turn tactic to move between two planar poses. Once the
robot places the fulcrum, it scans its surroundings for a lever and once located, approaches it
using the perception data. To minimize the effect of perception errors, once within 0.5 meters of
the lever, the robot deploys the wheel contact approach to position itself exactly in front of the
object and takes it back to the load. Finally, the robot positions the lever with Jacobian control
and exerts force with the top joint in its 7-dof arm.

\section{Experiments}

A significant challenge in accomplishing the series of the autonomous manipulation and perception
tasks has been the accumulation of error over the course of the executions. To remedy such an error
build-up, at the current state of our work, the authors intervene and instruct the robot to minimize
its position errors. We focus on the two main reasons and propose possible solutions.

During experiments, we observed that the RGBD data becomes more erroneous as the distance increases.
Within a 1 meter bound, the mean error is within 2-3 cm whereas with the maximum 4 meters (e.g. the
room limits), we see errors up to 10 cm. The proportional increase of error with respect to distance
suggest a camera calibration problem. Another source of error could be the slack in the tilt and pan
joints that control the camera view. The general of camera calibration has been addressed via bundle
adjustment in [2].

A second reason we suspect that might lead to localization errors is the error accumulated while the
robot attempts to follow a velocity profile in the forward direction. Figure \ref{fig:controller} demonstrates the
reference position and velocity trajectories (green), along with the real trajectories (red). To
remedy this error, we will focus on the trajectory following techniques developed by [7].

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.6\linewidth]{Figures/controller.png}
  \caption{The mechanical advantage in forces}
  \label{fig:controller}
\end{figure}

Lastly, the main experiment of our work is the successful overturning of the 45 kg obstacle. Figure
4 demonstrate the forces measured at the robot gripper as it pushes the lever until the obstacle
falls. Given that the load is approximately 500N and the maximum force is 250N, we observe an
advantage of 2:1.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.6\linewidth]{Figures/plot.png}
  \caption{The mechanical advantage in forces}
  \label{fig:plot}
\end{figure}

\section{Experimental Insights}

We offer two insights from our experiments. First, the manipulation of heavy objects brings about
interesting challenges. If the object inertia model is not known, the system can be thrown off
balance easily. Moreover, when the mass of the object is mostly on one of the wheels, the robot can
start spinning since one wheel has to accommodate the extra weight. Second, the constraint
optimization planner outputs too precise (e.g. 1$e^{-5}$) configurations which we observe clearly
cannot be executed to the same level of precision. We propose extending the planner for iterative
solutions and/or soft constraints.

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2014-05-15 exe/01-locateCinder.cpp

@@ -1,0 +1,440 @@
+/**
+ * @file 01-locateCinder.cpp
+ * @author Can Erdogan
+ * @date Feb 17, 2014
+ * @brief The robot locates the position of the cinder block wrt its own frame by moving its
+ * neck around and collecting the cinder block positions. Then, chooses the one that is closest.
+ */
+
+#include <kore.hpp>
+#include <kore/ik.hpp>
+#include <kore/safety.hpp>
+#include <kore/util.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+
+#define SQ(x) ((x) * (x))
+
+using namespace std;
+using namespace Krang;
+
+Vector7d lgoal, rgoal;
+
+/* ********************************************************************************************* */
+// State variables
+
+somatic_d_t daemon_cx;    
+ach_channel_t cinder_chan;
+somatic_motor_t* dynos;
+simulation::World* world;
+dynamics::SkeletonDynamics* krang;
+Hardware* hw;     
+
+bool dbg = false;
+bool resetInitPos = false;
+bool resetFinalArmPos = true;
+bool sending_commands = false;
+bool destroyAll = false;
+
+/* ******************************************************************************************** */
+void moveArmsOutOfPos (Vector7d& lgoal, Vector7d& rgoal) {
+
+	// First move the top two joints
+	Eigen::VectorXd lgoal2 = lgoal, rgoal2 = rgoal;
+	lgoal2(0) = lgoal2(1) = 0.0;
+	rgoal2(0) = rgoal2(1) = 0.0;
+	somatic_motor_setpos(&daemon_cx, hw->arms[LEFT], lgoal2.data(), 7);
+	somatic_motor_setpos(&daemon_cx, hw->arms[RIGHT], rgoal2.data(), 7);
+	while(true) {
+		somatic_motor_update(&daemon_cx, hw->arms[LEFT]);
+		somatic_motor_update(&daemon_cx, hw->arms[RIGHT]);
+		usleep(1e6);
+		if(((eig7(hw->arms[LEFT]->pos)-lgoal2).squaredNorm() < 0.005) &&
+			 ((eig7(hw->arms[RIGHT]->pos)-rgoal2).squaredNorm() < 0.005)) break;
+	}
+
[…]

### 2014-05-15 exe/02-navigateCinder.cpp

@@ -1,0 +1,230 @@
+/**
+ * @file 02-navigateCinder.cpp
+ * @author Can Erdogan
+ * @date Feb 13, 2014
+ * @brief 
+ * Does the following:
+ *  1) Stands up.
+ *  2) Given the cinder block configuration wrt robot, turns towards the desired Krang position next to it.
+ *  3) After initial turn is accomplished, gets data from the Kinect, updates the cinder block position.
+ *  4) Turns towards to Krang goal position again.
+ *  5) Move forward until it reaches that position (maybe a bit more back.)
+ *  6) Get data from Kinect. 
+ *  7) If in satisfactory range, jump to step 9.
+ *  8) If can reach the desired position by going forward, jump to 4).
+ *  9) Else, jump to 2).
+ * 10) Make a final turn to position itself parallel (+th=0.1) to the block. (Ignore any error and pray).
+ * 11) Sit down.
+ */
+
+#include "controllers.h"
+#include "vision.h"
+using namespace std;
+
+/* ******************************************************************************************** */
+somatic_d_t daemon_cx;				///< The context of the current daemon
+Krang::Hardware* krang;				///< Interface for the motor and sensors on the hardware
+simulation::World* world;			///< the world representation in dart
+ach_channel_t cinder_chan;
+
+bool dbg = false;
+
+/* ******************************************************************************************** */
+void init() {
+
+	// Populate the control each state needs
+	CTRL_MODE modes [] = {CTRL_BALANCE, CTRL_TURN, CTRL_BALANCE, CTRL_FORWARD, CTRL_BALANCE, 
+		CTRL_TURN, CTRL_BALANCE, CTRL_SIT};
+	for(size_t i = 0; i < 8; i++) stepCtrlModes[(STEP)i] = modes[i];
+
+	// Initialize the daemon
+	somatic_d_opts_t dopt;
+	memset(&dopt, 0, sizeof(dopt)); 
+	dopt.ident = "02-navigateCinder";
+	somatic_d_init(&daemon_cx, &dopt);
+
+	// Initialize the motors and sensors on the hardware and update the kinematics in dart
+	krang = new Krang::Hardware(Krang::Hardware::MODE_ALL_GRIPSCH, &daemon_cx, robot); 
+
+	// Check that the waist is at the expected angle
[…]

### 2014-05-15 exe/03-approachCinder-shorten.cpp

@@ -1,0 +1,103 @@
+/**
+ * @file 03-approachCinder-shorten.cpp
+ * @author Can Erdogan
+ * @date Feb 19, 2014
+ * @brief Shortens the path to reach to the cinder block.
+ */
+
+#include <kore.hpp>
+#include <kore/ik.hpp>
+#include <kore/safety.hpp>
+#include <kore/util.hpp>
+#include <planning/PathPlanner.h>
+#include <planning/PathShortener.h>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+#include <list>
+
+#define SQ(x) ((x) * (x))
+
+using namespace std;
+using namespace Krang;
+
+
+/* ********************************************************************************************* */
+// State variables
+
+simulation::World* world;
+dynamics::SkeletonDynamics* krang;
+Hardware* hw;     
+
+bool dbg = false;
+bool resetInitPos = false;
+bool sending_commands = false;
+bool halt = false;
+
+/* ********************************************************************************************* */
+Eigen::VectorXd robotConfig (32);
+Eigen::VectorXd cinderConfig (6);
+list <Eigen::VectorXd> path;
+
+/* ******************************************************************************************** */
+void readFile () {
+
+	fstream file ("path", fstream::in);
+	char line [1024];
+	file.getline(line, 1024);
+	std::stringstream stream(line, std::stringstream::in);
+	size_t i = 0;
+	double newDouble;
+	while (stream >> newDouble) robotConfig(i++) = newDouble;
+	i = 0;
+	file.getline(line, 1024);
+	std::stringstream stream2(line, std::stringstream::in);
+	while (stream2 >> newDouble) cinderConfig(i++) = newDouble;
+	while(file.getline(line, 1024)) {
+		i = 0;
+		Eigen::VectorXd config (7);
+		std::stringstream stream3(line, std::stringstream::in);
+		while (stream3 >> newDouble) config(i++) = newDouble;
+		path.push_back(config);
+	}
+}
+
+/* ******************************************************************************************** */
+int main () {
+
+	// Load scene
+	DartLoader dl;
+	world = dl.parseWorld("/etc/kore/scenes/04-World-Grasp.urdf");
+	assert((world != NULL) && "Could not find the world");
[…]

### 2014-05-15 exe/03-approachCinder.cpp

@@ -1,0 +1,334 @@
+/**
+ * @file 03-approachCinder-shorten.cpp
+ * @author Can Erdogan
+ * @date Feb 14, 2014
+ * @brief Meant to run on the vision computer by the main computer after a path is found.
+ */
+
+#include <kore.hpp>
+#include <kore/ik.hpp>
+#include <kore/safety.hpp>
+#include <kore/util.hpp>
+#include <planning/PathPlanner.h>
+#include <planning/PathShortener.h>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+#include <list>
+
+#define SQ(x) ((x) * (x))
+
+using namespace std;
+using namespace Krang;
+
+list <Eigen::VectorXd> path;
+
+/* ********************************************************************************************* */
+// State variables
+
+somatic_d_t daemon_cx;    
+ach_channel_t cinder_chan;
+simulation::World* world;
+dynamics::SkeletonDynamics* krang;
+Hardware* hw;     
+Eigen::Vector3d normal, hole;
+
+bool dbg = false;
+bool resetInitPos = false;
+bool sending_commands = false;
+bool halt = false;
+
+/* ******************************************************************************************** */
+/// Clean up
+void destroy() {
+	somatic_d_event(&daemon_cx, SOMATIC__EVENT__PRIORITIES__NOTICE, 
+	                SOMATIC__EVENT__CODES__PROC_STOPPING, NULL, NULL);
+	delete hw;
+	somatic_d_destroy(&daemon_cx);
+}
+
+/* ********************************************************************************************* */
+/// Get the mode input
+void *kbhit(void *) {
+	char input;
+	while(true){ 
+		input=cin.get(); 
+		if(input=='s') sending_commands = !sending_commands;
+		if(input=='h') {
+			halt = !halt;
+			if(halt) somatic_motor_halt(&daemon_cx, hw->arms[LEFT]);
+			else somatic_motor_reset(&daemon_cx, hw->arms[LEFT]);
+		}
+	}
+}
+
+/* ********************************************************************************************* */
+/// The main loop
+void run() {
+
+	// Start the daemon_cx running
[…]

### 2014-05-15 exe/04-pushCinder.cpp

@@ -1,0 +1,201 @@
+/**
+ * @file 02-refineApproach.cpp
+ * @author Can Erdogan
+ * @date Feb 16, 2014
+ * @brief Performs Jacobian inverse kinematics to refine the gripper location by +-5 cm.
+ */
+
+#include <kore.hpp>
+#include <kore/workspace.hpp>
+#include <kore/display.hpp>
+#include <kore/util.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+
+/* ********************************************************************************************* */
+// Type declarations
+
+/* ********************************************************************************************* */
+// Constants
+
+// initializers for the workspace control constants
+const double K_WORKERR_P = 1.00;
+const double NULLSPACE_GAIN = 0.1;
+const double DAMPING_GAIN = 0.005;
+bool negateDir = false;
+
+// various rate limits - be nice to other programs
+
+using namespace std;
+
+/* ********************************************************************************************* */
+// State variables
+
+// hardware objects
+Krang::Hardware* hw;                                   ///< connects to hardware
+
+// process state
+somatic_d_t daemon_cx;                          ///< daemon context
+ach_channel_t cinder_chan;
+
+// pointers to important DART objects
+simulation::World* world;
+dynamics::SkeletonDynamics* krang;
+bool dbg = false;
+
+// workspace stuff
+Krang::WorkspaceControl* workspace;
+Krang::Vector7d nullspace_q_ref; ///< nullspace configurations for the arms
+Krang::Vector7d nullspace_q_mask; ///< nullspace configurations for the arms
+
+// cinder block
+Eigen::Vector3d normal;
+
+/* ******************************************************************************************** */
+/// Clean up
+void destroy() {
+	somatic_d_event(&daemon_cx, SOMATIC__EVENT__PRIORITIES__NOTICE, 
+	                SOMATIC__EVENT__CODES__PROC_STOPPING, NULL, NULL);
+	delete workspace;
+	delete hw;
+	somatic_d_destroy(&daemon_cx);
+
+}
[…]

### 2014-05-15 exe/05-prepareBrickStand.cpp

@@ -1,0 +1,234 @@
+/**
+ * @file 03-standUp.cpp
+ * @author Can Erdogan
+ * @date Feb 16, 2014
+ * @brief Krang brings the cinder block to its front and stands up.
+ */
+
+#include <kore.hpp>
+#include <kore/workspace.hpp>
+#include <kore/display.hpp>
+#include <kore/util.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+
+using namespace std;
+using namespace Krang;
+
+Krang::Hardware* hw;                                   ///< connects to hardware
+somatic_d_t daemon_cx;        
+simulation::World* world;
+dynamics::SkeletonDynamics* krang;
+somatic_motor_t* larmTop;
+ach_channel_t cinder_chan;
+bool dbg = false;
+
+/* ******************************************************************************************** */
+void increaseWaistAngle () {
+	cout << "Moving the waist? Ready? " << endl;
+	getchar();
+	Somatic__WaistCmd *waistDaemonCmd = somatic_waist_cmd_alloc();		
+	somatic_waist_cmd_set(waistDaemonCmd, SOMATIC__WAIST_MODE__REAL_CURRENT_MODE);
+	while(true) {
+
+		// Send a current value
+		double current = -2.5;
+		somatic_vector_set_data(waistDaemonCmd->data, &current, 1);
+		int r = SOMATIC_PACK_SEND(hw->waistCmdChan, somatic__waist_cmd, waistDaemonCmd);
+		if(ACH_OK != r) fprintf(stderr, "Couldn't send message: %s\n", 
+			ach_result_to_string(static_cast<ach_status_t>(r)));
+
+		// Update the state and see if we can stop
+		hw->updateSensors(1e-2);
+		cout << hw->waist->pos[0] << endl;
+		if(hw->waist->pos[0] < 2.618) {
+			somatic_waist_cmd_set(waistDaemonCmd, SOMATIC__WAIST_MODE__STOP);
+			int r = SOMATIC_PACK_SEND(hw->waistCmdChan, somatic__waist_cmd, waistDaemonCmd);
+			if(ACH_OK != r) fprintf(stderr, "Couldn't send message: %s\n", 
[…]

### 2014-05-15 exe/05-standUp.cpp

@@ -1,0 +1,309 @@
+/**
+ * @file 03-standUp.cpp
+ * @author Can Erdogan
+ * @date Feb 16, 2014
+ * @brief Krang brings the cinder block to its front and stands up.
+ */
+
+#include <kore.hpp>
+#include <kore/workspace.hpp>
+#include <kore/display.hpp>
+#include <kore/util.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+
+using namespace std;
+using namespace Krang;
+
+Krang::Hardware* hw;                                   ///< connects to hardware
+somatic_d_t daemon_cx;        
+simulation::World* world;
+dynamics::SkeletonDynamics* krang;
+somatic_motor_t* larmTop;
+ach_channel_t cinder_chan;
+
+Vector6d K_stand, K_bal;
+Vector6d state0;	
+bool dbg = false;
+bool start = false;
+
+pthread_mutex_t mutex = PTHREAD_MUTEX_INITIALIZER;
+int locoMode = 1;
+
+/* ******************************************************************************************** */
+/// Read file for gains
+void readGains () {
+
+	// Get the gains
+	Vector6d* kgains [] = {&K_stand, &K_bal};
+	ifstream file ("/home/cerdogan/Documents/Software/project/krang/iser/data/gains-03.txt");
+	assert(file.is_open());
+	char line [1024];
+	for(size_t k_idx = 0; k_idx < 2; k_idx++) {
+		*kgains[k_idx] = Vector6d::Zero();
+		file.getline(line, 1024);
+		std::stringstream stream(line, std::stringstream::in);
+		size_t i = 0;
+		double newDouble;
+		while ((i < 6) && (stream >> newDouble)) (*kgains[k_idx])(i++) = newDouble;
+	}
+	cout << "K_stand: " << K_stand.transpose() << endl;
+	cout << "K_bal: " << K_bal.transpose() << endl;
+	file.close();
+}
+
+/* ******************************************************************************************** */
+/// Clean up
+void destroy() {
+	somatic_d_event(&daemon_cx, SOMATIC__EVENT__PRIORITIES__NOTICE, 
[…]

### 2014-05-15 exe/06-moveCinder.cpp

@@ -1,0 +1,239 @@
+/**
+ * @file 06-navigateCinder.cpp
+ * @author Can Erdogan
+ * @date Feb 13, 2014
+ * @brief 
+ * Does the following:
+ *  1) Stands up.
+ *  2) Given the cinder block configuration wrt robot, turns towards the desired Krang position next to it.
+ *  3) After initial turn is accomplished, gets data from the Kinect, updates the cinder block position.
+ *  4) Turns towards to Krang goal position again.
+ *  5) Move forward until it reaches that position (maybe a bit more back.)
+ *  6) Get data from Kinect. 
+ *  7) If in satisfactory range, jump to step 9.
+ *  8) If can reach the desired position by going forward, jump to 4).
+ *  9) Else, jump to 2).
+ * 10) Make a final turn to position itself parallel (+th=0.1) to the block. (Ignore any error and pray).
+ * 11) Sit down.
+ */
+
+#include "controllers.h"
+#include "vision.h"
+using namespace std;
+
+/* ******************************************************************************************** */
+somatic_d_t daemon_cx;				///< The context of the current daemon
+Krang::Hardware* krang;				///< Interface for the motor and sensors on the hardware
+simulation::World* world;			///< the world representation in dart
+ach_channel_t cinder_chan;
+
+bool dbg = false;
+bool startWithTurn = true;
+
+/* ******************************************************************************************** */
+void init() {
+
+	// Populate the control each state needs
+	CTRL_MODE modes [] = {CTRL_BALANCE, CTRL_TURN, CTRL_BALANCE, CTRL_FORWARD, CTRL_BALANCE, 
+		CTRL_TURN, CTRL_BALANCE, CTRL_SIT};
+	for(size_t i = 0; i < 8; i++) stepCtrlModes[(STEP)i] = modes[i];
+
+	// Initialize the daemon
+	somatic_d_opts_t dopt;
+	memset(&dopt, 0, sizeof(dopt)); 
+	dopt.ident = "06-moveCinder";
+	somatic_d_init(&daemon_cx, &dopt);
+
+	// Initialize the motors and sensors on the hardware and update the kinematics in dart
+	krang = new Krang::Hardware(Krang::Hardware::MODE_ALL_GRIPSCH, &daemon_cx, robot); 
+
+	// Check that the waist is at the expected angle
[…]

### 2014-05-15 exe/07-pickLever.cpp

@@ -1,0 +1,272 @@
+/**
+ * @file 07-pickLever.cpp
+ * @author Can Erdogan
+ * @date Feb 20, 2014
+ * @brief Drives towards a lever while sitting down on the ground and detects when both wheels
+ * are against the lever by checking encoder values being the same (torque 25Nm seems good).
+ * Then uses left arm to pick up the lever using a predefined configuration (after backing up
+ * by 0.60 degrees on both wheels).
+ */
+
+#include <kore.hpp>
+#include <kore/workspace.hpp>
+#include <kore/display.hpp>
+#include <kore/util.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+
+using namespace std;
+using namespace Krang;
+
+// initializers for the workspace control constants
+const double K_WORKERR_P = 1.00;
+const double NULLSPACE_GAIN = 0.1;
+const double DAMPING_GAIN = 0.005;
+Krang::WorkspaceControl* workspace;
+Krang::Vector7d nullspace_q_ref; ///< nullspace configurations for the arms
+Krang::Vector7d nullspace_q_mask; ///< nullspace configurations for the arms
+
+ach_channel_t cinder_chan;
+Krang::Hardware* krang;                                   ///< connects to hardware
+somatic_d_t daemon_cx;                          ///< daemon context
+simulation::World* world;
+dynamics::SkeletonDynamics* robot;
+bool dbg = false;
+
+enum MODE {
+	MakeContact = 0,
+	BackUp,
+	PrepareArm1,
+	PrepareArm2,
+	ReachObject,
+	GrabObject,
+	PullUp,
+	TakeFront
+};
+
+/* ******************************************************************************************** */
+/// Clean up
+void destroy() {
+	somatic_d_event(&daemon_cx, SOMATIC__EVENT__PRIORITIES__NOTICE, 
+	                SOMATIC__EVENT__CODES__PROC_STOPPING, NULL, NULL);
+	delete workspace;
+	delete krang;
+	somatic_d_destroy(&daemon_cx);
+}
+
[…]

### 2014-05-15 exe/08-placeLever.cpp

@@ -1,0 +1,320 @@
+/**
+ * @file 08-placeLever.cpp
+ * @author Can Erdogan
+ * @date Feb 20, 2014
+ * @brief Krang places the lever using only f/t data and the design parameters.
+ */
+
+#include <kore.hpp>
+#include <kore/workspace.hpp>
+#include <kore/display.hpp>
+#include <kore/util.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+
+using namespace std;
+using namespace Krang;
+
+double bla;
+
+
+// initializers for the workspace control constants
+const double K_WORKERR_P = 1.00;
+const double NULLSPACE_GAIN = 0.1;
+const double DAMPING_GAIN = 0.005;
+Krang::WorkspaceControl* workspace;
+Krang::Vector7d nullspace_q_ref; ///< nullspace configurations for the arms
+Krang::Vector7d nullspace_q_mask; ///< nullspace configurations for the arms
+
+ach_channel_t cinder_chan;
+Krang::Hardware* krang;                                   ///< connects to hardware
+somatic_d_t daemon_cx;                          ///< daemon context
+simulation::World* world;
+dynamics::SkeletonDynamics* robot;
+Eigen::Vector3d normal, hole;
+bool dbg = false;
+
+enum MODE {
+	GoDown = 0,
+	GoRight,
+	GoLeft,
+	OpenHand,
+	GoLeft2,
+	CloseHand,
+	GoUp,
+};
+
+/* ******************************************************************************************** */
+/// Clean up
+void destroy() {
+	somatic_d_event(&daemon_cx, SOMATIC__EVENT__PRIORITIES__NOTICE, 
+	                SOMATIC__EVENT__CODES__PROC_STOPPING, NULL, NULL);
+	delete workspace;
+	delete krang;
+	somatic_d_destroy(&daemon_cx);
+}
+
+/* ********************************************************************************************* */
+/// The main loop
+void run() {
+
+	// start some timers
+	double time_last = aa_tm_timespec2sec(aa_tm_now());
+	MODE mode = GoDown;
+	MODE lastMode = mode;
[…]

### 2014-05-15 exe/09-push.cpp

@@ -1,0 +1,626 @@
+/**
+ * @file 09-push.cpp
+ * @author Can Erdogan
+ * @date Feb 16, 2014
+ * @brief Pushing the lever task: (1) back up away from the design on the ground, (2) fix the arms,
+ * (3) stand up, (4) increase waist angle, (5) which induces another balance state with different
+ * gains, wait there for a little while to stabilize, (6) get vision date about the tip of the
+ * lever, (7) reach out to tip, (8) grasp, (9) go down wait waist until 165 degs and (10)
+ * balance low (just like stand up).
+ */
+
+#include <kore.hpp>
+#include <kore/workspace.hpp>
+#include <kore/display.hpp>
+#include <kore/util.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+
+using namespace std;
+using namespace Krang;
+
+fstream mylog;
+
+// initializers for the workspace control constants
+const double K_WORKERR_P = 1.00;
+const double NULLSPACE_GAIN = 0.1;
+const double DAMPING_GAIN = 0.005;
+Krang::WorkspaceControl* workspace;
+Krang::Vector7d nullspace_q_ref; ///< nullspace configurations for the arms
+Krang::Vector7d nullspace_q_mask; ///< nullspace configurations for the arms
+
+Krang::Hardware* krang;                                   ///< connects to hardware
+somatic_d_t daemon_cx;        
+simulation::World* world;
+dynamics::SkeletonDynamics* robot;
+ach_channel_t chan;
+ach_channel_t cinder_chan;
+
+Vector7d K_stand, K_bal;			// extra for com offset
+Vector6d state0;	
+bool dbg = false;
+bool start = false;
+
+Somatic__WaistCmd *waistDaemonCmd = somatic_waist_cmd_alloc();		
+
+pthread_mutex_t mutex = PTHREAD_MUTEX_INITIALIZER;
+
+enum Step {
+	STEP_BACKUP = 0,
+	STEP_FIXARMS,
+	STEP_STANDUP,
+	STEP_WAIST,
+	STEP_STABILIZE,
+	STEP_VISION,
+	STEP_REACHOUT,
+	STEP_GRASP,
+	STEP_PUSH,
+	STEP_REST
+};
+
+enum CtrlMode {
+	CTRL_GROUND = 0,
[…]

### 2014-05-15 exe/10-navigateLever.cpp

@@ -1,0 +1,229 @@
+/**
+ * @file 02-navigateCinder.cpp
+ * @author Can Erdogan
+ * @date Feb 13, 2014
+ * @brief 
+ * Does the following:
+ *  1) Stands up.
+ *  2) Given the cinder block configuration wrt robot, turns towards the desired Krang position next to it.
+ *  3) After initial turn is accomplished, gets data from the Kinect, updates the cinder block position.
+ *  4) Turns towards to Krang goal position again.
+ *  5) Move forward until it reaches that position (maybe a bit more back.)
+ *  6) Get data from Kinect. 
+ *  7) If in satisfactory range, jump to step 9.
+ *  8) If can reach the desired position by going forward, jump to 4).
+ *  9) Else, jump to 2).
+ * 10) Make a final turn to position itself parallel (+th=0.1) to the block. (Ignore any error and pray).
+ * 11) Sit down.
+ */
+
+#include "controllers.h"
+#include "vision.h"
+using namespace std;
+
+/* ******************************************************************************************** */
+somatic_d_t daemon_cx;				///< The context of the current daemon
+Krang::Hardware* krang;				///< Interface for the motor and sensors on the hardware
+simulation::World* world;			///< the world representation in dart
+ach_channel_t cinder_chan;
+
+bool dbg = false;
+
+/* ******************************************************************************************** */
+void init() {
+
+	// Populate the control each state needs
+	CTRL_MODE modes [] = {CTRL_BALANCE, CTRL_TURN, CTRL_BALANCE, CTRL_FORWARD, CTRL_BALANCE, 
+		CTRL_TURN, CTRL_BALANCE, CTRL_SIT};
+	for(size_t i = 0; i < 8; i++) stepCtrlModes[(STEP)i] = modes[i];
+
+	// Initialize the daemon
+	somatic_d_opts_t dopt;
+	memset(&dopt, 0, sizeof(dopt)); 
+	dopt.ident = "02-navigateCinder";
+	somatic_d_init(&daemon_cx, &dopt);
+
+	// Initialize the motors and sensors on the hardware and update the kinematics in dart
+	krang = new Krang::Hardware(Krang::Hardware::MODE_ALL_GRIPSCH, &daemon_cx, robot); 
+
+	// Check that the waist is at the expected angle
[…]

### 2014-05-15 exe/11-putCinder.cpp

@@ -1,0 +1,187 @@
+/**
+ * @file 11-putCinder.cpp
+ * @author Can Erdogan
+ * @date Feb 16, 2014
+ * @brief Krang places the cinder block to its front.
+ */
+
+#include <kore.hpp>
+#include <kore/workspace.hpp>
+#include <kore/display.hpp>
+#include <kore/util.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <iomanip>
+
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+
+#include <somatic/msg.h>
+
+using namespace std;
+using namespace Krang;
+
+Krang::Hardware* hw;                                   ///< connects to hardware
+somatic_d_t daemon_cx;        
+simulation::World* world;
+dynamics::SkeletonDynamics* krang;
+somatic_motor_t* larmTop;
+ach_channel_t cinder_chan;
+bool dbg = false;
+
+/* ******************************************************************************************** */
+void decreaseWaistAngle () {
+	Somatic__WaistCmd *waistDaemonCmd = somatic_waist_cmd_alloc();		
+	somatic_waist_cmd_set(waistDaemonCmd, SOMATIC__WAIST_MODE__REAL_CURRENT_MODE);
+	while(true) {
+
+		// Send a current value
+		double current = 0.0;
+		if(hw->waist->pos[0] < 2.3) current = 0.1;
+		else if(hw->waist->pos[0] < 2.62) current = 0.0;
+		else current = -0.02;
+		somatic_vector_set_data(waistDaemonCmd->data, &current, 1);
+		int r = SOMATIC_PACK_SEND(hw->waistCmdChan, somatic__waist_cmd, waistDaemonCmd);
+		if(ACH_OK != r) fprintf(stderr, "Couldn't send message: %s\n", 
+			ach_result_to_string(static_cast<ach_status_t>(r)));
+
+		// Update the state and see if we can stop
+		hw->updateSensors(1e-2);
+		cout << hw->waist->pos[0] << endl;
+		if(hw->waist->pos[0] > 2.75) {
+			somatic_waist_cmd_set(waistDaemonCmd, SOMATIC__WAIST_MODE__STOP);
+			int r = SOMATIC_PACK_SEND(hw->waistCmdChan, somatic__waist_cmd, waistDaemonCmd);
+			if(ACH_OK != r) fprintf(stderr, "Couldn't send message: %s\n", 
[…]

### 2014-05-15 scripts/getData.sh

@@ -1,0 +1,37 @@
+#!/bin/sh
+
+killall achd
+rm -rf /dev/shm/ach*
+
+ach -o 666 -C imu-data || exit 1
+ach -o 666 -C waist-state || exit 1
+ach -o 666 -C amc-state || exit 1
+ach -o 666 -C dynamixel-state || exit 1
+ach -o 666 -C dynamixel-cmd || exit 1
+ach -o 666 -C cinder || exit 1
+ach -o 666 -C llwa-state || exit 1
+ach -o 666 -C rlwa-state || exit 1
+ach -o 666 -C amc-cmd || exit 1
+ach -o 666 -C llwa-cmd || exit 1
+ach -o 666 -C rlwa-cmd || exit 1
+ach -o 666 -C waistd-cmd || exit 1
+ach -o 666 -C waist-cmd || exit 1
+ach -o 666 -C lgripper-state|| exit 1
+ach -o 666 -C lgripper-cmd || exit 1
+ach -o 666 -C rgripper-state|| exit 1
+ach -o 666 -C rgripper-cmd || exit 1
+ach -o 666 -C llwa_ft
+ach -o 666 -C rlwa_ft
+ach -o 666 -C torso-state
+ach -o 666 -C torso-cmd
+ach -o 666 -C event
+
+achd -r pull 192.168.1.51 imu-data -d   
+achd -u 10000 -r pull 192.168.1.51 waist-state -d
+achd -u 10000 -r pull 192.168.1.51 amc-state -d 
+achd -u 10000 -r pull 192.168.1.51 dynamixel-state -d
+achd -r pull 192.168.1.51 cinder -d 
+achd -u 10000 -r pull 192.168.1.51 llwa-state -d 
+achd -u 10000 -r pull 192.168.1.51 rlwa-state -d 
+achd -u 10000 -r pull 192.168.1.51 llwa_ft -d 
+achd -u 10000 -r pull 192.168.1.51 rlwa_ft -d 

### 2014-05-15 src/bla.c

@@ -1,0 +1,327 @@
+/**
+ * @file 01-rotate.cpp
+ * @author Can Erdogan
+ * @date Feb 13, 2014
+ * @brief Demonstrates the autonomous turn-in-place behavior. The robot stands up, turns 90
+ * degrees left or right, and sits down, using encoder values.
+ * Note that for the robot to turn th degrees in place, each wheel needs to do (th * R / r)
+ * radians of rotation. R is the radius of rotation and r is the wheel radius.
+ */
+
+
+#include <iostream>
+#include <fstream>
+
+#include <Eigen/Dense>
+
+#include <kore.hpp>
+
+#include <dynamics/SkeletonDynamics.h>
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+#include <initModules.h>
+#include <kinematics/BodyNode.h>
+#include <math/UtilsRotation.h>
+
+
+typedef Eigen::Matrix<double,6,1> Vector6d;
+
+using namespace std;
+
+somatic_d_t daemon_cx;				///< The context of the current daemon
+Krang::Hardware* krang;				///< Interface for the motor and sensors on the hardware
+simulation::World* world;			///< the world representation in dart
+dynamics::SkeletonDynamics* robot;			///< the robot representation in dart
+
+static const double wheelRadius = 0.264;	// r, cm
+static const double rotationRadius = 0.350837; // R, cm
+Vector6d K_stand, K_bal, K_turn_left, K_turn_right;
+Vector6d state0;	///< in the beginning of entering mode 2
+bool start = false;
+bool dbg = false;
+bool shouldRead = false;
+double extraSpin = 0.0;
+size_t integralWindow = 0;
+double Ksint, intErrorLimit;
+double offsetAngle = 0.0;
+
+pthread_mutex_t mutex = PTHREAD_MUTEX_INITIALIZER;
+size_t mode = 0;		// 0 sitting, 1 standing up, 2 stable, 3 turning, 4 sitting down
+
+/* ******************************************************************************************** */
+/// Read file for gains
+void readGains () {
+
+	// Get the gains
+	Vector6d* kgains [] = {&K_stand, &K_bal, &K_turn_left, &K_turn_right};
[…]

### 2014-05-15 src/controllers.cpp

@@ -1,0 +1,328 @@
+/**
+ * @file controllers.cpp
+ * @author Can Erdogan
+ * @date Feb 18, 2014
+ * @brief Contains the controller information for the balancing acts.
+ */
+
+#include "controllers.h"
+
+using namespace Krang;
+using namespace std;
+
+Eigen::VectorXd K_bal (6);
+Eigen::VectorXd K_turn (9);
+Eigen::VectorXd K_forw (6);
+std::map <STEP, CTRL_MODE> stepCtrlModes;
+dynamics::SkeletonDynamics* robot;			///< the robot representation in dart
+bool changePermitted = false;
+bool firstDetect = true;
+bool start = false, done = false, nextStep = false;
+bool startOver = false;
+double extraUForw = 0;
+double extraUSpin = 0;
+bool withCinder;
+
+/* ******************************************************************************************** */
+bool controller (STEP step, Vector6d state, double dt, const Eigen::Vector3d& motionParams) { 
+
+	if(dbg) DISPLAY_VECTOR(motionParams);
+
+	// Get the integral parameters for turning
+	size_t integralWindow = (int) K_turn(6);
+	double Ksint = K_turn(7), intErrorLimit = K_turn(8);
+	static vector <double> spinErrors;
+	static int balancedCounter = 0;
+	static int turnCounter = 0;
+	static int forwardCounter = 0;
+	static int spinIdx = 0;
+	CTRL_MODE ctrlMode = stepCtrlModes[step];
+	if((spinIdx == 0) && (ctrlMode == CTRL_TURN)) {
+		for(size_t i = 0; i < integralWindow; i++)
+			spinErrors.push_back(0.0);
+	}
+
+	// Define the variables for velocity profiles
+	static const double acceleration = 0.008;		
+	static const double deceleration = 0.008;	
+	static const double maxVel = 0.12;	
+	static double accTime = -1.0;
+	static double decTime = -1.0;
+	static double cruiseTime = -1.0;
+
+	// Determine if the step has changed. If so, set the initial state, state0. Or increment time.
+	static double ctrlTime = 0.0;
+	static Vector6d state0 = state;
+	static STEP lastStep = step;
+	if(step != lastStep) {
[…]

### 2014-05-15 src/controllers.h

@@ -1,0 +1,93 @@
+/**
+ * @file controllers.cpp
+ * @author Can Erdogan
+ * @date Feb 18, 2014
+ * @brief Contains the controller information for the balancing acts.
+ */
+
+#pragma once
+
+#include <iostream>
+#include <fstream>
+
+#include <Eigen/Dense>
+
+#include <kore.hpp>
+
+#include <dynamics/SkeletonDynamics.h>
+#include <robotics/parser/dart_parser/DartLoader.h>
+#include <simulation/World.h>
+#include <kinematics/BodyNode.h>
+#include <math/UtilsRotation.h>
+#include <map>
+
+using namespace Krang;
+
+extern double extraUForw;
+extern bool done;
+extern bool firstDetect;
+extern bool nextStep;
+extern double extraUSpin;
+extern bool dbg;
+extern bool start;
+extern bool startOver;
+extern bool changePermitted;
+extern bool withCinder;
+
+/* ******************************************************************************************** */
+extern somatic_d_t daemon_cx;				///< The context of the current daemon
+extern Krang::Hardware* krang;				///< Interface for the motor and sensors on the hardware
+extern simulation::World* world;			///< the world representation in dart
+extern dynamics::SkeletonDynamics* robot;			///< the robot representation in dart
+extern ach_channel_t cinder_chan;
+
+/* ******************************************************************************************** */
+/// To represent the state machine which chooses Kinect and wheel actions
+enum STEP {
+	STEP_STANDUP = 0,
+	STEP_TURN_1 = 1,
+	STEP_TURN_DETECT_1 = 2,
+	STEP_FORWARD = 3,
+	STEP_FORWARD_DETECT = 4,
+	STEP_TURN_2 = 5,
+	STEP_TURN_DETECT_2 = 6,
+	STEP_SIT = 7
+};
+
+/// To decide which control is in charge of the robot torques
+enum CTRL_MODE {
+	CTRL_BALANCE = 0,
+	CTRL_TURN = 1,
+	CTRL_FORWARD = 2,
+	CTRL_SIT = 3
+};
+
+/// The specification of control mode for each step 
+extern std::map <STEP, CTRL_MODE> stepCtrlModes;
+
+/* ********************************************************************************************* */
+// Functions
+
+/// Exerts torques to the wheel in accordance with the desired control mode and state; returns
+/// true if the error is within the bounds specified for the specific mode
+bool controller (STEP step, Vector6d state, double dt, const Eigen::Vector3d& motionParams); 
+
[…]

### 2014-05-15 src/vision.cpp

@@ -1,0 +1,217 @@
+/**
+ * @file vision.cpp
+ * @author Can Erdogan
+ * @date Feb 18, 2014
+ * @brief Contains the vision related helper functions.
+ */
+
+#include <Eigen/Dense>
+#include <vector>
+#include "controllers.h"
+#include <fstream>
+
+using namespace std;
+
+/* ******************************************************************************************** */
+/// Determines the turn angles and the distance the robot should go from its current state
+Eigen::Vector3d loadToPose (const Eigen::VectorXd& load) {
+
+	static const bool debug = 1;
+
+	// Determine the three values
+	Eigen::Vector3d planeCenter = load.block<3,1>(0,0);
+	Eigen::Vector3d dir = load.block<3,1>(3,0);
+	if(debug) cout << "planeCenter: " << planeCenter.transpose() << endl;
+	if(debug) cout << "dir: " << dir.transpose() << endl;
+	Eigen::Vector3d perp (-dir(1), dir(0), 0.0);
+	Eigen::Vector3d goalPos = planeCenter - 1.2 * dir + 0.38 * perp; 
+	Eigen::Vector3d normal = perp;
+	if(debug) cout << "goalPos: " << goalPos.transpose() << endl;
+	if(debug) cout << "normal: " << normal.transpose() << endl;
+	double th2 = M_PI_2 + atan2(-goalPos(0), goalPos(1));
+	double th = (M_PI_2 + atan2(normal(0), -normal(1)) + 0.2) - th2;
+	if(debug) cout << "th: " << th << ", th2: " << th2 << endl;
+
+	// Change angles to wheel encoders using the wheel radius and the rotation radius
+	static const double wheelRadius = 0.264;	// r, cm
+	static const double rotationRadius = 0.350837; // R, cm
+	double v1 = (th2 * rotationRadius) / wheelRadius;
+	double v3 = (th * rotationRadius) / wheelRadius;
+
+	// Change the distance to the goal position to encoder values
+	double dist = sqrt(goalPos(0) * goalPos(0) + goalPos(1) * goalPos(1));
+	if(debug) cout << "dist: " << dist << endl;
+	double v2 = dist / wheelRadius;
+	Eigen::Vector3d params (v1,v2,v3);
+	if(debug) cout << "params: " << params.transpose() << endl;
+	return params;
+}
+
+
+/* ******************************************************************************************** */
[…]

### 2014-05-15 src/vision.h

@@ -1,0 +1,32 @@
+/**
+ * @file vision.h
+ * @author Can Erdogan
+ * @date Feb 18, 2014
+ * @brief Contains the vision related helper functions.
+ */
+
+#include <Eigen/Dense>
+#include <vector>
+#include "controllers.h"
+
+/// Determines the turn angles and the distance the robot should go from its current state
+Eigen::Vector3d loadToPose (const Eigen::VectorXd& load);
+
+/// Determines the turn angles and the distance the robot should go from its current state
+Eigen::Vector3d cinderToPose (const Eigen::VectorXd& cinder);
+
+/// Finds the consensus in the data and interprets it to get the motion parameters. Returns the
+/// consensus data
+Eigen::VectorXd analyzeKinectData (const std::vector <Eigen::VectorXd>& data, bool extra = true);
+
+/// Reads the vector data coming from the vision computer
+bool getVecData (ach_channel_t& chan, Eigen::VectorXd& data);
+
+/// Reads the cinder block data coming from the vision computer and returns it in the robot frame
+/// (e.g. the initial robot frame at time 0).
+bool getCinder (Eigen::VectorXd& data);
+bool getLoad (Eigen::VectorXd& data);
+
+/// Read data from the localization executable
+Eigen::VectorXd readCinderData ();
+

### 2014-05-15 tests/00-visualize.cpp

@@ -1,0 +1,250 @@
+/**
+ * @author Can Erdogan
+ * @file 00-visualize.cpp
+ * @date Feb 19, 2014
+ * @brief Visualizes the scene using the ach channels from Krang.
+ */
+
+#include <collision/CollisionDetector.h>
+#include <collision/fcl_mesh/FCLMESHCollisionDetector.h>
+#include <dynamics/ConstraintDynamics.h>
+#include <planning/PathPlanner.h>
+#include <planning/PathShortener.h>
+
+#include <kore/ik.hpp>
+#include <kore/safety.hpp>
+#include <kore/simTab.hpp>
+#include <kore/util.hpp>
+#include <kore.hpp>
+
+#include "vision.h"
+
+using namespace Krang;
+using namespace std;
+
+bool dbg = false;
+Hardware* krang;
+somatic_d_t daemon_cx;    
+ach_channel_t cinder_chan;
+dynamics::SkeletonDynamics* robot;
+somatic_motor_t* dynos;
+list <Eigen::VectorXd> path;
+Eigen::VectorXd ql0;
+Vector7d theta;
+bool armSet = false;
+
+/* ********************************************************************************************* */
+/// Application class
+extern wxNotebook* tabView;
+class mainApp : public GRIPApp {
+	virtual void AddTabs() {
+		tabView->AddPage(new SimTab(tabView), wxT("-"));
+	}
+};
+
+IMPLEMENT_DYNAMIC_CLASS(SimTab, GRIPTab)
+DECLARE_APP(mainApp)
+IMPLEMENT_APP(mainApp)
+
+/* ********************************************************************************************* */
+/// Detects collisions with the environment and within robot
+struct timespec t_now, t_prev;	///< for timing each iteration
+void Timer::Notify() {
+
+	static vector <Eigen::VectorXd> data;
+
+	// Get the current time and compute the difference
+	t_now = aa_tm_now();
+	double dt = (double) aa_tm_timespec2sec(aa_tm_sub(t_now, t_prev));
+	t_prev = t_now;
+
+	// Get data from the ach channels
+	krang->updateSensors(dt);
+
+	// Do the collision checking
+	bool collision = mWorld->checkCollision(false);
+
+	// Set the background
+	if(collision) {
+		glClearColor(1.0, 0.0, 0.0 ,1.0f);
+		float fogCol[3] = {1.0, 0.0, 0.0};
[…]

### 2014-05-15 tests/01-grasp.cpp

@@ -1,0 +1,165 @@
+/**
+ * @file 01-grasp.cpp
+ * @author Can Erdogan
+ * @date Feb 15, 2014
+ * @brief Perform analytical I.K. to get a joint configuration and then use RRT to find a
+ * collision-free, shortened trajectory.
+ */
+
+#include <collision/CollisionDetector.h>
+#include <collision/fcl_mesh/FCLMESHCollisionDetector.h>
+#include <dynamics/ConstraintDynamics.h>
+#include <planning/PathPlanner.h>
+#include <planning/PathShortener.h>
+
+#include <kore/ik.hpp>
+#include <kore/safety.hpp>
+#include <kore/simTab.hpp>
+#include <kore/util.hpp>
+
+using namespace Krang;
+using namespace std;
+
+dynamics::SkeletonDynamics* krang;
+list <Eigen::VectorXd> path;
+Eigen::VectorXd ql0;
+
+/* ********************************************************************************************* */
+/// Application class
+extern wxNotebook* tabView;
+class mainApp : public GRIPApp {
+	virtual void AddTabs() {
+		tabView->AddPage(new SimTab(tabView), wxT("-"));
+	}
+};
+
+IMPLEMENT_DYNAMIC_CLASS(SimTab, GRIPTab)
+DECLARE_APP(mainApp)
+IMPLEMENT_APP(mainApp)
+
+/* ********************************************************************************************* */
+/// Detects collisions with the environment and within robot
+void Timer::Notify() {
+
+	// Do the collision checking
+	bool collision = mWorld->checkCollision(false);
+
+	// Set the background
+	if(collision) {
+		glClearColor(1.0, 0.0, 0.0 ,1.0f);
+		float fogCol[3] = {1.0, 0.0, 0.0};
+		glFogfv(GL_FOG_COLOR,fogCol);
+	}
+	else viewer->setClearColor();
+	viewer->DrawGLScene();
+	
+	// If there is no path, just wait
+	if(path.empty()) {
+		Start(0.01 * 1e3);	
+		return;
+	}
+
+	// Traverse the path
+	static size_t pathIdx = 0;
+	krang->setConfig(left_arm_ids, *(path.begin()));
+	path.pop_front();
+	viewer->DrawGLScene();
+	Start(0.01 * 1e3);	
+}
+
+
+/* ********************************************************************************************* */
+SimTab::SimTab(wxWindow *parent, const wxWindowID id, const wxPoint& pos, const wxSize& size, 
[…]

### 2014-05-15 tests/02-navigate.cpp

@@ -1,0 +1,142 @@
+/**
+ * @file 02-navigate.cpp
+ * @author Can Erdogan
+ * @date Feb 18, 2014
+ * @brief Given the cinder block and Krang configuration, shows the angle Krang should rotate to,
+ * the distance it should travel and finally rotate again, to reach the cinder block and perform
+ * I.K.
+ */
+
+#include <collision/CollisionDetector.h>
+#include <collision/fcl_mesh/FCLMESHCollisionDetector.h>
+#include <dynamics/ConstraintDynamics.h>
+#include <planning/PathPlanner.h>
+#include <planning/PathShortener.h>
+
+#include <kore/ik.hpp>
+#include <kore/safety.hpp>
+#include <kore/simTab.hpp>
+#include <kore/util.hpp>
+
+using namespace Krang;
+using namespace std;
+
+dynamics::SkeletonDynamics* krang;
+
+/* ********************************************************************************************* */
+/// Application class
+extern wxNotebook* tabView;
+class mainApp : public GRIPApp {
+	virtual void AddTabs() {
+		tabView->AddPage(new SimTab(tabView), wxT("-"));
+	}
+};
+
+IMPLEMENT_DYNAMIC_CLASS(SimTab, GRIPTab)
+DECLARE_APP(mainApp)
+IMPLEMENT_APP(mainApp)
+
+/* ********************************************************************************************* */
+SimTab::SimTab(wxWindow *parent, const wxWindowID id, const wxPoint& pos, const wxSize& size, 
+		long style) : GRIPTab(parent, id, pos, size, style) {
+
+	// Setup environment
+  sizerFull = new wxBoxSizer(wxHORIZONTAL);
+	wxBoxSizer* sizerFull = new wxBoxSizer (wxHORIZONTAL);
+	viewer->camRadius = 5.0;
+	viewer->camRotT << 0.0, 1.0, 0.0, 0.0, 0.0, 1.0, 1.0, 0.0, 0.0;
+	viewer->worldV << 0.35, -0.1, 0.0;
+	viewer->UpdateCamera();
+	SetSizer(sizerFull);
+	frame->DoLoad("/etc/kore/scenes/04-World-Grasp.urdf");
+	wxGetApp().setConfiguration("/etc/kore/scenes/configs/01-standUp.config");
+	krang = mWorld->getSkeleton("Krang");
+	Krang::setupKrangCollisionModel(mWorld, krang);
+
[…]

### 2014-05-23 doc/paper/paper.tex
..

@@
 \documentclass[runningheads,a4paper]{llncs}
-
+% \documentclass{article}
 \usepackage{amssymb}
+\usepackage{amsmath}
 \setcounter{tocdepth}{3}
@@
 \usepackage{url}
+\usepackage[algoruled, vlined,linesnumbered]{algorithm2e}
 
@@
 \institute{Institute for Robotics and Intelligent Machines \\Georgia Institute of Technology}
-
 \maketitle
@@
 
+\newpage
 \section{Technical Approach}
 
-We now present our approach to autonomous construction of simple machines, particularly a
-lever-fulcrum assembly to overturn heavy obstacles, in four major categories: (1) autonomous design,
-(2) visual perception, (3) posture control, and (4) motion planning.
+\subsection{Constraint Satisfaction for Simple Machine Designs}
 
-In any design, components have to be placed to satisfy a set of physical or domain constraints. For
-instance, a candidate 2-by-4 block needs to make contact both with the load and the fulcrum,
-essentially distance functions between objects, to satisfy physical constraints of the design.
-However, for a design to be useful, we also impose that the contact point for the lever is further
-away from the fulcrum than the load such that a mechanical advantage is achieved. In previous work,
-we propose a nonlinear optimization approach where such geometric and dynamic constraints are
-expressed as equality and inequality functions whose common zero-crossings are design configurations
-that satisfy all the constraints. For this work, we use the planner to output the lever and the
-fulcrum configurations, and the required contact point, but allow the robot to choose its closest
-configuration, assuming it can supply the necessary force.
+The manipulation of multiple objects to achieve a goal can be readily represented in a constraint
+satisfaction paradigm where the constraints represent the relationships between the design
+components. In this work, we focus on simple machine designs such as lever-fulcrum assemblies or
+inclined planes that need to be structurally stable and provide mechanical leverage to their users.
+Reasoning about such design criteria requires analysis of more detailed concepts such as center
+of masses, robot kinodynamic constraints and physics principles.
 
-In perceiving the environment, we propose using a light-weight feature-based recognition approach as
-opposed to full 3D based approaches that use the entire mesh data such as the iterative closest
-point algorithm or over-segmentation methods. The key assumption of the work is that the planner
-already knows the mesh of the available objects and with minimal additional feature knowledge, such
-as the top of a cinder block is at 44 cm from the ground or a lever is at least 2 meters in one
-dimension, we can speed up detection. At its current stage, the agent can autonomously detect cinder
-blocks, the load as shown in Figure 1, the walls and the 2-by-4 levers. To localize objects of
-interest, we perform a simple scan with the tilt and pan degrees of freedom of the RGBD camera,
-taking also into account the robot kinematics. Figure \ref{fig:detection} demonstrates the detection module.
+The process for an autonomous planner is composed of three steps. First, from the set of available objects
+in the environment, it needs to choose a subset that will be incorporated in the structure. Second,
+the structure components are assigned roles that designate how they should be put together - specifically,
+the constraints that \textit{bind} one to another. Lastly, the planner needs to configure the objects
+such that the role constraints and the general design criteria are satisfied.
+
+\subsubsection{Component Choices}
+
+A completeness property for an autonomous planner for structural designs is a crucial advantage
+for deployment in real-world circumstances (e.g. military or search-and-rescue operations). In
+emergency situations, when physically challenging that requires creative reasoning about simple
+machines usually arise, the ability to exhaustively search for all possible solutions and determine
+if one exists is a critical advantage. Note that we assume every object is used only once in the 
+structure as opposed to the agent changing the structure as its being used.
+
+In choosing a set of design components, an autonomous planner needs to exhaustively search the 
+entire \textit{finite} space of discrete assignments. In comparison to continuous choices, such as
+object configurations, the discrete nature of the choices (i.e. in or out) makes such a search
+feasible. Despite the finite space, it is challenging to evaluate
+every alternative since there is still a combinational number of roles and infinite 
+space of configurations to reason about.
+
+To remedy the computational challenge, pruning strategies and heuristics are significant tools in
+cutting back the search at the top level. For instance, in construction a lever-fulcrum design,
+two wooden blocks of the same size (or approximately to a degree of confidence) can be categorized
+under one class. Similarly, for loads that are known to be significantly heavier than a robot can
+handle, the longer lever candidates might be priotized in the search process.
+
+\subsubsection{Object Roles}
+
+Imagine a two-step stairs is needed to enable a swarm of rough-terrain vehicles, such as 
+PackBots or RHexs \cite{yamauchi2004packbot,saranli2001rhex}, climb a window and survey a building, and some of them have robotic
+arms that can stack box-like objects. The goal for a planner would be to choose three boxes and
+stack two of them (e.g. box B on C) such that the swarm can first climb one step and then move on to
+the two stack, until it reaches the window sill.
+
+In coming up with this solution, two types of choices need to made. First, among the three objects,
+say A, B, and C, which object would constitute as the first step and which one would be at the top
+in the second step needs to be decided. Secondly, to place the objects on the ground or on top of
+another object, a base face needs to be chosen to clarify the object roles and to simplify the
+representation of the constraints for the object configurations. Note that choosing a base 
+in fact partitions the configuration space of the objects even before the design constraints
+are considered to prune infeasible assignments.
+
+The goal of the object roles is to specify (1) the relationship of a component with respect to
+others, and (2) which of its face and edges are used in these connections. Figure \ref{fig:matches} 
+\cite{erdogan2014incorporating} demonstrates some outcome assemblies with the triangle prism
+object acting as fulcrum positioned on different base faces and in contact with the chosen lever
+on various edges. Similarly, we observe that the lever can be used on at least two of its faces
+(discounting symmetries) while it is still possible to find a feasible assembly.
 
@@
   \centering
-  \includegraphics[width=1.0\linewidth]{Figures/detection.png}
-  \caption{The mechanical advantage in forces}
+  \includegraphics[width=0.7\linewidth]{Figures/matches.png}
+  \caption{Different face and edge assignments for the lever-fulcrum assembly. Some assignments,
+  such as using the shortest edge of the lever to connect the fulcrum and the load, may not
+  be feasible due to design constraints and collisions.}
+  \label{fig:matches}
+\end{figure}
+
+The role assignment to available resources has been a thoroughly studied area, starting from
+classical planning \cite{newell1961gps,mccarthy1963programs}, and evolving into operations research
+\cite{fulkerson1961network,taha1975integer}, and in this work, we adopt the STRIPS representation
+for the planning process \cite{fikes1972strips}. The idea is to provide the domain knowledge of possible
+actions to take on the available objects in the environment. For instance, a lever can be \textit{placed}
+on a fulcrum or a ramp can be \textit{rested} against another object. A minor difference in our
+framework is that every action induces additional constraints to the assembly configurations and
+an action can be taken if and only if there exists some configuration that satisfies the accumulated
+constraints.
+
+\subsubsection{Continuous Configuration Space and Constraints}
+
+The proposed framework accumulates design constraints via a classical planning framework
+and a feasibility process determines whether the constraints can be satisfied by some configuration
+of the components. The idea is that the different type of constraints can all be generically
+expressed as equality or inequality functions on the space of object and robot configurations.
+If all the constraints are convex, for instance in a stair or bridge design with simplified
+robot assumptions, the feasibility can be determined by an efficient simplex algorithm
+implementation \cite{erdogan2013planning}. For the larger set of nonconvex domains, especially when
+robot kinodynamics are considered, we propose a nonlinear optimization process which minimizes the
+violation of the constraints and attempts to find an assignment of configurations that satisfies all of them.
+
+A number of design constraints such as stacking a box on top of another one or placing a lever
+at the edge of a fulcrum can be expressed with geometric projections. Figure \ref{fig:constraints}
+demonstrates three types of connections: (1) center of mass-face, (2) edge-face, and (3) face-face. 
+The general idea is that points of interest such as center of mass, endpoints of an edge or vertices
+of a face are projected to the plane of another face and limits are imposed on its location. For instance,
+for two objects to be stacked successfully (A), the center of mass of the top object has to lie within
+the supporting face of the bottom object. Similarly, to ensure an edge is on a face (B), it is sufficient
+to confine the endpoints of the edge onto the face plane and guarantee there exists a shared point
+(e.g. cross) between the edge and the face. Lastly, for contact between two faces (C), 
+three points of one of the faces has to lie on the other one and again, a shared point should exist.
+Observe that geometric contact concepts are easily expressed through equality
+and inequality expressions on the projections of significant points on the meshes.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=0.75\linewidth]{Figures/constraints.png}
+  \caption{Visualization of different types of geometric contact constraints}
+  \label{fig:constraints}
+\end{figure}
+
+Once the object choices and roles are determined, the equality and the inequality constraints between
+the assembly components can be gathered into two sets $\mathcal{F}$ and $\mathcal{G}$ respectively.
+The idea behind using optimization to find feasible samples in the configuration space is based on
+creating error functions by the violation of the constraints for a sample $\vec{x}$:
+
+\vspace{-1em}
+\begin{align*}
+f(\vec{x}) = 0 \;\; \Rightarrow & \;\; E_f(\vec{x}) = f^2(\vec{x}) \\
+g(\vec{x}) \leq 0 \;\; \Rightarrow & \;\; E_g(\vec{x}) = 
+	\begin{cases}
+		g^2(\vec{x}) & \text{if $g(\vec{x}) > 0 $}, \\
+	0        & \text{otherwise}.
+	\end{cases}
+\end{align*}
+
+\noindent where $E_f(\vec{x})$ and $E_g(\vec{x})$ are the proposed squared error functions. Now,
+given the constraint sets $\mathcal{F}$ and $\mathcal{G}$, we define the total error:
+
+\begin{equation}
+	\mathcal{E}(\vec{x}) = \sum\limits_{f \in \mathcal{F}} E_f(\vec{x}) + \sum\limits_{g \in \mathcal{G}} E_g(\vec{x}).
+\end{equation}
+
+\noindent Note that $\mathcal{E}(\vec{x})$ is 0 for
+some $\vec{x}$ if and only if configurations $\vec{x}$ satisfy all the design
+constraints. Moreover, the global minima is guaranteed be more than or equal
+to 0 since the function is a sum of squared errors. Then, by using an optimization method, such as
+Levenberg-Marquardt, the global minima could be found through sampling the space for good initializations.
+
+We outline the overall approach in Algorithm 1 below. Given the available objects, the goal
+criteria and the available actions, the planner searches in the space of discrete object roles
+(line 3) and attempts to take actions as long as they lead to feasible configurations (line 9). The forward
+search accumulates constraints until a feasible design is reached or backtracks.
+
+\begin{algorithm}[ht!]
+  \SetCommentSty{emph}
+  \KwIn{$domain$: objects properties and generic actions; $goals$: list of goal literals to be fulfilled; $initialState$: discrete literals and no constraints; }
+  \KwResult{configurations: a feasible value in goal subspace; }
+  $stateStack \leftarrow $createStack$(initialState);$ \\
+  \While{$state \leftarrow stateStack$.pop$()$} {
+    $actions \leftarrow $stateActions$(domain)$; \\
+    \ForEach{$action$ in the set $actions$} {
+      \If{$action.pres \subset state.literals$} {
+				newConsts $\leftarrow$ state.consts $\cup$ action.consts; \\
+				\For{$counter = 1 \dots MAX\_COUNT$} {
+					\{\textit{localMin, confs}\} $\leftarrow $optimize($newConsts$, newSeed($domain$)); \\
+					\If{abs$(localMin) \leq 1e^{-4}$} {
+						\lIf{$goals \subset action.afters$} \Return{confs}; \\
+						\Else{
+							$child = \{state.literals \cup action.afters, newConsts\}$ \\
+							$stateStack$.push($child$); \\
+							\textbf{break}; \\
+						}
+					}
+				}
+			}
+		}
+  }
+  \Return{$\emptyset$}; 
+  \caption{ConstraintPlanner()}
+\end{algorithm}
+
+\subsection{Humanoid Robot Platform: Golem Krang}
+
+Designed and built in the Humanoid Robotics Laboratory, Golem Krang is a 150 kg, 6.2 m segway-like
+humanoid robot with two wheels that uses a balancing strategy for locomotion and manipulation \cite{stilman2010golem}.
+Given its unique design, an autonomous planner for functional structures needs to address several
+hardware constraints. First, the contact point on the lever needs to be reachable by the robot.
+Second, the robot needs to apply sufficient force to overcome the opposing weight or friction. For
+Golem Krang, we opt to use only the waist and the wheel motors (Figure 1), and choose to fix the
+arms with hard mechanical breaks. The motivation is three-fold: (1) the chosen joints have
+sufficient torque to actuate the simple machine, (2) simpler reasoning about reachable space of the
+end-effectors, and (3) hardware safety in manipulating hundreds of kgs of objects with an already
+heavy robot. Lastly, Golem Krang needs to maintain a stable posture before contact is made with the
+structure.
+
+\subsection{Perception}
+
+Equipped with a two degree of freedom platform that houses a Microsoft Kinect, Golem Krang can
+inspect and reason about its environment with visual data. In perceiving the environment, we propose
+using a light-weight feasure-based recognition approach as opposed to full 3D based approaches that
+use the entire mesh data such as the iterative closest point algorithm or over-segmentation methods.
+Figure \ref{fig:detection} demonstrates a sample output of the framework.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=0.9\linewidth]{Figures/detection.png}
+  \caption{Cinder block and wooden plates detected as fulcrum and lever objects.}
   \label{fig:detection}
@@
 
-For the locomotion controllers, we model Krang as a simple inverse pendulum and use a
-proportional-derivative control with gain scheduling for different robot poses to minimize the
-frequency of oscillations in dynamic balancing. In picking up cinder blocks, the torque around the
-wheel axis due to the additional force at the end-effector is incorporated in computing the goal
-balancing angle.
+The key assumption of the work is that the planner already knows the mesh of the available objects
+and with minimal additional feature knowledge, such as the top of a cinder block is at 44 cm from
+the ground or a lever is at least 2 meters in one dimension, we can speed up the detection. At its
+current stage, the agent can autonomously detect cinder blocks, the load as shown in Figure 1, the
+walls and the 2-by-4 levers. To localize objects of interest, we perform a simple scan with the tilt
+and pan degrees of freedom of the RGBD camera, taking also into account the robot kinematics.
 
-Lastly, for motion planning, we use a variety of approaches. First, to grasp objects, we use
-analytical inverse kinematics to determine if there is a configuration close to the object we can
-reach without collisions. Once close, we perform Jacobian inverse kinematics to approach the object
-and detect contact with the object with the gripper force-torque sensor. Analytical inverse
-kinematics is used as a resolution-complete method to determine whether a collision-free grasp
-configuration exists as opposed to sampling the large configuration space of the arms to avoid local
-minima with Jacobians. In addition to motion planning for the arms, we also make use of an example
-of conformant planning in picking up a lever. The motivation is to avoid perception problems by
-running each wheel to the 2-by-4 on the ground while the wheels cannot exert the torque to climb
-over the object. Thus, the robot autonomously aligns itself with the object of interest by using
-contact points without the need for precise perception.
+\subsection{Locomotion}
 
-\section{Results}
+% Why balance?
+% How to balance? 
+% How to balance while carrying objects?
 
-Our results demonstrate Golem Krang autonomously construct a simple machine design, specifically a
-lever-fulcrum assembly, and use it to overturn a 45 kg load. To achieve such an autonomous behavior,
-we propose a set of modules that accomplish object detection and localization, balancing and
-navigation controller in the presence of external disturbances, and a rich set of motion planning
-modules. To demonstrate the execution of the task, we designed the following scenario (see
-\url{http://tinyurl.com/mw2ehxl} for video):
-
-We position Golem Krang in the middle of the room and instruct it to use the closest cinder block as
-a fulcrum. Using the aforementioned tools, the robot picks up the object (e.g. reacts to its weight
-by leaning backwards) and carries it to the predetermined position instructed by the constraint
-optimization planner. During locomotion, we assume that there are no obstacles on the path of the
-robot, and the robot uses the turn-forward-turn tactic to move between two planar poses. Once the
-robot places the fulcrum, it scans its surroundings for a lever and once located, approaches it
-using the perception data. To minimize the effect of perception errors, once within 0.5 meters of
-the lever, the robot deploys the wheel contact approach to position itself exactly in front of the
-object and takes it back to the load. Finally, the robot positions the lever with Jacobian control
-and exerts force with the top joint in its 7-dof arm.
-
-\section{Experiments}
-
-A significant challenge in accomplishing the series of the autonomous manipulation and perception
-tasks has been the accumulation of error over the course of the executions. To remedy such an error
-build-up, at the current state of our work, the authors intervene and instruct the robot to minimize
-its position errors. We focus on the two main reasons and propose possible solutions.
-
-During experiments, we observed that the RGBD data becomes more erroneous as the distance increases.
-Within a 1 meter bound, the mean error is within 2-3 cm whereas with the maximum 4 meters (e.g. the
-room limits), we see errors up to 10 cm. The proportional increase of error with respect to distance
-suggest a camera calibration problem. Another source of error could be the slack in the tilt and pan
-joints that control the camera view. The general of camera calibration has been addressed via bundle
-adjustment in [2].
-
-A second reason we suspect that might lead to localization errors is the error accumulated while the
-robot attempts to follow a velocity profile in the forward direction. Figure \ref{fig:controller} demonstrates the
-reference position and velocity trajectories (green), along with the real trajectories (red). To
-remedy this error, we will focus on the trajectory following techniques developed by [7].
-
-\begin{figure}[ht!] 
-  \centering
-  \includegraphics[width=0.6\linewidth]{Figures/controller.png}
-  \caption{The mechanical advantage in forces}
-  \label{fig:controller}
-\end{figure}
-
-Lastly, the main experiment of our work is the successful overturning of the 45 kg obstacle. Figure
-4 demonstrate the forces measured at the robot gripper as it pushes the lever until the obstacle
-falls. Given that the load is approximately 500N and the maximum force is 250N, we observe an
-advantage of 2:1.
-
-\begin{figure}[ht!] 
-  \centering
-  \includegraphics[width=0.6\linewidth]{Figures/plot.png}
-  \caption{The mechanical advantage in forces}
-  \label{fig:plot}
-\end{figure}
-
-\section{Experimental Insights}
-
-We offer two insights from our experiments. First, the manipulation of heavy objects brings about
-interesting challenges. If the object inertia model is not known, the system can be thrown off
-balance easily. Moreover, when the mass of the object is mostly on one of the wheels, the robot can
-start spinning since one wheel has to accommodate the extra weight. Second, the constraint
-optimization planner outputs too precise (e.g. 1$e^{-5}$) configurations which we observe clearly
-cannot be executed to the same level of precision. We propose extending the planner for iterative
-solutions and/or soft constraints.
-
+\newpage
 \bibliographystyle{plain}
@@
 \end{document}
+
+% DISCUSSION: CHALLENGES WITH VISUAL SERVOING A NONHOLONOMIC ROBOT BASE
+
+% Having chosen the objects and their roles, the autonomous planner needs to find configurations
+% for the assembly components to satisfy a range of constraints. First, the proposed assembly needs
+% to be physically stable (e.g. all center of masses of upper layers within support polygons) and 
+% collision-free. Second, the structure should satisfy its purpose, such as overturning a load,
+% while taking into account the actuator robot's kinodynamic limitations, possibly guided by design
+% principles such as the input arm of a lever being longer than the load arm for mechanical advantage.
+% Note that in considering the robot limitations, we focus on the initial moment of actuation where
+% presumably the required force input is maximal and output a robot configuration and required joint
+% torques along with the design that is sufficient to realize the task.

### 2014-05-23 doc/paper/paper.tex
..

@@
 
+The primary locomotion strategy for Golem Krang is to balance on its two wheels, keeping its
+center of mass on the vertical plane through its wheel axis. Modeled as an inverted pendulum,
+locomotion via balancing has a few advantages over running on both the wheels and the back caster of
+the robot. First, the footprint of the robot is smaller, 54 cm front to back due to diameter
+of the wheels while dynamically balancing as opposed to 86 cm when the robot is staticly grounded.
+Second, the locomotion of the robot is simpler to model since the fixed caster without omnidirectional
+wheels has different friction properties as the robot spins, moves forward and backward.
+
+The position and posture control is implemented using a proportional derivative controller based on
+the inertial readings that indicate the robot angle from the vertical and the wheel encoders. In
+this work, we assume the environment is setup such that the locomotion can be carried out by
+turning towards the goal position, moving forward and adjusting for the goal orientation - ignoring
+collisions in the world. To move forward, we use a velocity profile with limits on minimum and maximum
+acceleration and deceleration.
+
+A significant aspect of the locomotion is the manipulation of heavy objects such as 15 kg cinder
+blocks and 10 kg wooden plates. To enable stable dynamic balancing, the force-torque sensors
+at the end-effectors of Golem Krang are used to incorporate the mass of the carried objects into
+the robot model and update the center of mass position appropriately using forward kinematics. We
+provide additional insights on heavy object manipulation in the experiments section, specifically
+on the effect of the object inertia and mass on the system stability.
+
+\subsection{Manipulation}
+
 % Why balance?

### 2014-05-23 doc/paper/paper.tex
Added manip picture

@@
 the robot. First, the footprint of the robot is smaller, 54 cm front to back due to diameter
-of the wheels while dynamically balancing as opposed to 86 cm when the robot is staticly grounded.
+of the wheels while dynamically balancing, as opposed to 86 cm when the robot is staticly grounded.
 Second, the locomotion of the robot is simpler to model since the fixed caster without omnidirectional
-wheels has different friction properties as the robot spins, moves forward and backward.
+wheels has different ground friction properties as the robot spins, moves forward and backward.
 
@@
 
-% Why balance?
-% How to balance? 
-% How to balance while carrying objects?
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=1.0\linewidth]{Figures/manipulation.png}
+  \caption{.}
+  \label{fig:manipulation}
+\end{figure}
+
+asdf
 

### 2014-05-24 doc/bla.m
Got the data

@@ -1,0 +1,35 @@
+data=load('mydata');
+figure(1);
+clf
+fts = [];
+for i = 1 : size(data,1)
+  fts(end+1) = norm(data(i,1:3));
+end
+fts = -data(:,3);
+%plot(data(:,1), 'r'); hold on;
+%plot(data(:,2), 'g'); hold on;
+%plot(data(:,3), 'b'); hold on;
+plot((1:277)/277*14.6, fts(1224:1500), 'r', 'LineWidth', 3); hold on;
+plot((1:277)/277*14.6, 200 * data((1224:1500),9), 'b', 'LineWidth', 3); hold on;
+curs = [];
+for i = 1 : size(data,1)
+  curs(end+1) = 10 * norm(data(i,[10,13,15]));
+  %curs(end+1) = 10 * norm(data(i,10:16));
+  if(i < 1200)
+    curs(end) = 0;
+  end
+end
+curs = curs(1224:1500);
+plot((1:277)/277*14.6, curs, 'g', 'LineWidth', 3); hold on;
+title('End-Effector Force/Position and Mean Joint Current for Small Lever Task', 'FontSize', 18);
+set(gcf,'color','w');
+xlabel('Time (secs)', 'FontSize', 15);
+ylabel('Sensor reading ()', 'FontSize', 15);
+legend('Vertical force reading (Nm)', 'End-effector Vertical Position (cm)', 'Average Current (dA)', 'Location', 'NorthWest');
+%plot(data(:,10), 'k'); hold on;
+%plot(data(:,11), 'k'); hold on;
+%plot(data(:,12), 'k'); hold on;
+%plot(data(:,13), 'k'); hold on;
+%plot(data(:,14), 'k'); hold on;
+%plot(data(:,15), 'k'); hold on;
+%plot(data(:,16), 'k'); hold on;

### 2014-05-26 doc/paper/paper.tex
taking screenshots

@@
 Figure \ref{fig:detection} demonstrates a sample output of the framework.
+% TODO Justify why not use planar segmentation and ICP
 
@@
 
+The manipulation of multiple objects under motor and perception uncertainty requires a series of 
+robust strategies both algorithmicly and in practical implementation. In this work, a wide range of
+motion planning tools are adopted such as rapidly-expanding random trees (RRTs) \cite{kuffner2000rrt},
+analytical inverse kinematics \cite{tolani2000real} and Jacobian control \cite{whitney1969resolved}. 
+Additionally, to handle perception errors, we propose using guarded moves \cite{bejczy1977effect} 
+that control the manipulator behavior until a predetermined tactile feedback is received. Moreover,
+we deploy ``conformant motion'' behaviors where the robot action forces itself
+and its environment to a desired state without any sensory feedback \cite{goldman1996expressive}.
+
+\subsubsection{Motion planning}
+
+Figure \ref{fig:manipulation} depicts the analytical inverse kinematics and the motion planning
+steps during the manipulation of a cinder block to be used as a fulcrum. We use a predetermined
+grasp location, the top surface with the holes at the sides (see Figure \ref{fig:manipulation}a).
+Having observed the object and moved its base to a desirable configuration, the goal for Golem
+Krang is to use one of its manipulators to grasp the object. To do so, we first use analytical
+inverse kinematics to find configurations close to the object we can reach without collisions.
+Figure \ref{fig:manipulation}a displays three configurations out of which the left most,
+semi-transparent one collides with one of the wheels. Once a goal in arm jointspace is determined,
+bidirectional RRTs with path shortening and smoothing are used to move the arm from its initial 
+pose to the goal. Figure \ref{fig:manipulation}b demonstrates the keyframes as the left arm moves
+around the cinder block to avoid collisions until it reaches the goal pose (green) in front of the grasp point.
+
 \begin{figure}[ht!] 
@@
   \includegraphics[width=1.0\linewidth]{Figures/manipulation.png}
-  \caption{.}
+  \caption{Left: Candidate grasp poses for the block - left most in collision with wheel.
+  Right: RRT trajectory to goal grasp pose, moving around the block to avoid collisions.}
   \label{fig:manipulation}
@@
 
-asdf
+\vspace{-2em}
+\subsubsection{Guarded and conformant motions}
+
+Once in position using motion planning, Golem Krang uses force/torque feedback at the end-effectors
+to reach out to the cinder block until contact and ensure its grippers can grasp it. Such guarded
+moves have proven to be simple, heuristic alternatives to visual servoing as the robot picks up
+levers, and positions them on the fulcrum and inside the load.
+
+In addition to guarded moves with sensory feedback, we also utilize conformant motions where
+in order to localize the lever more precisely, the robot runs its wheels against the lever,
+usually one of them first, turning its base flush against it and eliminating any visual positioning error.
+Such motions have been used before to eliminate uncertainty in the initial configuration of manipulated
+objects in assembly tasks by pushing the objects into known configurations. \cite{mason1986mechanics}
+
+\section{Experiments}
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=1.0\linewidth]{Figures/asdf.png}
+  \caption{The mechanical advantage in forces}
+  \label{fig:showOff}
+\end{figure}
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=1.0\linewidth]{Figures/asdfg.png}
+  \caption{The mechanical advantage in forces}
+  \label{fig:showOff}
+\end{figure}
+
+% The robot has to move its arms out of the way to visualize the objects.
 

### 2014-05-26 doc/paper/paper.tex
Got the initial draft of the pictures with arrows. Next: Remove text
finished the typical run figure. next: weight shift figure
results ve discussion kaldi

@@
 \usepackage[algoruled, vlined,linesnumbered]{algorithm2e}
+\usepackage{color}
 
@@
 and its environment to a desired state without any sensory feedback \cite{goldman1996expressive}. 
-
+% 
 \subsubsection{Motion planning}
@@
 
-\begin{figure}[ht!] 
-  \centering
-  \includegraphics[width=1.0\linewidth]{Figures/asdf.png}
-  \caption{The mechanical advantage in forces}
-  \label{fig:showOff}
-\end{figure}
+Golem Krang is tasked with overturning a 45 kg load using a lever-fulcrum assembly with a limit of
+\textcolor{red}{TBA} Nm on the force it can apply to the environment. Given the dimensions of the 
+available objects in the environment, the robot has to design a structure, locate the components,
+configure them into their positions and actuate the simple machine. In the following section, we
+describe a typical run, focusing on details of perception, locomotion and manipulation.
+
+Placed in a random configuration in the room, Golem Krang begins by scanning the room for the 
+available objects and find the closest cinder block that would be used as a fulcrum (see Figure \ref{fig:typical_a}).
+The scanning process is composed of a set of atomic behaviors which allow the robot to raise
+its torso while sitting on the ground and move its arms out of its sight to avoid occlusions.
+Once the fulcrum is located, the robot starts balancing and approaching the robot, until it 
+positions itself in a predetermined distance to grasp the object. Using the motion planning tools,
+such as RRTs and guarded moves, the robot grasps the cinder block at its top.
 
@@
   \centering
-  \includegraphics[width=1.0\linewidth]{Figures/asdfg.png}
-  \caption{The mechanical advantage in forces}
-  \label{fig:showOff}
+  \includegraphics[width=1.0\linewidth]{Figures/a.png}
+  \caption{Once Golem Krang detects the closest cinder block (left), it approaches (middle) and grasps
+  the objects (right). Scene continues in Figure \ref{fig:typical_b}.}
+  \label{fig:typical_a}
 \end{figure}
 
-% The robot has to move its arms out of the way to visualize the objects.
+An interesting observation we expand on in Section 4 is about how the location of a manipulated object
+and the uneven distribution of its weight over the wheels affect the locomotion accuracy. To minimize
+such an artifact, in Figure \ref{fig:typical_b}, Golem Krang first moves the grasped cinder block 
+to the middle of its torso before turning around and localizing the load object at 45 kg. Having
+detected the load, the final configuration of the fulcrum is deduced from the assembly design and
+the robot places it appropriately.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=1.0\linewidth]{Figures/b.png}
+  \caption{Having grasped the fulcrum, the robot localizes the load and places the fulcrum
+		in the initial design configuration. Scene continues in Figure \ref{fig:typical_c}.} 
+	\label{fig:typical_b}
+\end{figure}
+
+In the third part of the experiment, Golem Krang needs to detect and localize a candidate lever
+object and grasp it, as shown in Figure \ref{fig:typical_c}. Given the size of the lever and the
+noisy perception data, we propose using the wheels to localize the lever object more accurately
+once the robot approaches it. Figure \ref{fig:typical_c}b displays the conformant behavior where the 
+robot moves forward slowly to collide with the lever and have its localization error fixed. The
+left wheel first makes contact and the contact overcomes the input torque, while the right wheel 
+keeps moving until the robot is parallel and directly in front of the lever.
+
+\begin{figure}[ht!]  	
+  \centering
+  \includegraphics[width=1.0\linewidth]{Figures/c.png}
+  \caption{The lever is picked up by first using vision and then running
+	the wheels against the object to make physical contact before manipulation. Scene continues 
+	in Figure \ref{fig:typical_d}.}
+  \label{fig:typical_c}
+\end{figure}
+
+To simplify the locomotion, we have assumed collision-free paths and when Golem Krang carries the
+lever, we ensure that the lever is carried high enough that it does not collide with other objects
+(see Figure \ref{fig:typical_d}. Once the robot repositions itself in front of the robot, using
+guarded moves, the robot first pushes the lever against the load horizontal to ensure it is at
+the correct horizontal distance and then raises it until the design specification. Once at the
+correct height, the robot releases the lever and allows it to slide on the fulcrum into the load
+ - one of the more practically challenging tasks. For addition tasks, we have used task-constraint
+ manipulation with online perception to minimize the errors during this routine. Finally, in
+ Figure \ref{fig:typical_d}c, the robot pushes the object at the desired contact point and overturns
+it.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=1.0\linewidth]{Figures/d.png}
+  \caption{The mechanical advantage in forces}
+  \label{fig:typical_d}
+\end{figure}
+
+\section{Results}
+
+In this section, we provide experimental results on the functionality of the realized simple
+machines under different conditions, study the sources of inaccuracies in the assembly process
+and provide some insights on the autonomous manipulation of heavy objects.
+
+\subsection{Designs with Different Load Weights and Lever Choices}
 

### 2014-05-26 doc/paper/abstract.tex
exp first figure done

%\documentclass[runningheads,a4paper]{llncs}
\documentclass{article}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}

\begin{document}

% \mainmatter

\title{Autonomous Realization of Simple Machines}
\author{Can Erdogan \and Mike Stilman}
% \institute{Institute for Robotics and Intelligent Machines \\Georgia Institute of Technology}

\maketitle

\begin{abstract}

For robots to become integral parts of human daily experi- ence, they need to be able to utilize the
objects in their environment to accomplish any range of tasks. In this work, we focus particularly
on physically challenging tasks that push the limits on the robot kinodynamic constraints such as
joint limits, joint torques and etc. Previously, we demonstrated an autonomous planner that
instructs a human collab- orator where to place the available objects in the environment to form a
simple machine such as a lever-fulcrum assembly. In this work, we report results on the autonomous
realization of such a design by the humanoid robot Golem Krang, focusing on the challenges of
autonomous perception, manipulation and control.

\end{abstract}

\section{Introduction}

The ability to use the available objects in the environment towards accomplishing goals is essential
to thriving in challenging circumstances. Everyday examples of tool use include simple machines such
as levers and pulleys. The challenge in autonomous design of such simple machines is the space of
discrete choices for the component options and the related high-dimensional continuous configuration
space of the chosen components.

In previous work \cite{erdogan2013planning} \cite{erdogan2014incorporating}, we demonstrated the
constraint satisfaction approach to assembly design, specifically for robotic manipulation and
locomotion. The key idea is to represent the constraints
between the components of the design, the robot kinematics and dynamics as generic equality and
inequality functions within a nonlinear optimization framework and solve for the global minima, if
necessary by random restarts. Such global optimization methods have been used in other fields as
well, such as operations research \cite{vidal2006branching} and architecture \cite{yu2011make}.

In this work, we take the next step towards full autonomy where the humanoid robot, Golem Krang,
autonomously manipulates the objects in its environment to construct a simple machine. We present
an autonomous planner that perceives the available objects, specifically 15 kg cinder blocks and 10
kg 2-by-4 block blocks (e.g. potential levers), relocates them to the desired configurations output
by the constraint planner, and actuates them to flip a 45 kg load. Figure \ref{fig:showOff} demonstrates key scenes
from this scenario such as (a) detection of a cinder block, (b) locomotion with a heavy load, (c)
manipulating a lever while subject to multiple constraints and (d) application of force to the lever
leading to a successful load motion.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/showOff.png}
  \caption{The mechanical advantage in forces}
  \label{fig:showOff}
\end{figure}

Significant effort has been demonstrated by \cite{beetz2010cram} \cite{stilman2005navigation}
\cite{kemp2007challenges} to incorporate autonomous agents in human environments. Our work stands
out in multiple aspects from the established state of the art. First, Golem Krang is a two-wheeled
balancing robot, similar to a segway with two 7-dof robotic arms installed. The challenge with
such a platform is the dynamic stability constraint where the robot has to ensure its center of mass
is close to the wheel axis at all times as opposed to legged or multi-wheeled platforms. Secondly, to the best of our knowledge,
Golem Krang is the tallest and heaviest two-wheeled robot with 150 kg at 1.9 m, a unique property
among similar designs \cite{kuindersma2009dexterous}. As we expand in Section IV, at this scale, the
weight can help with heavy-duty manipulation but complicates the autonomous locomotion of the
agent. Lastly, Golem Krang perceives its environment with an onboard RGBD sensor with two degrees
of freedom that are manipulated autonomously for gaze control. Autonomous perception and scene
recognition has only recently started to gather interest in the humanoid robotics field
\cite{srinivasa2010herb} \cite{nishiwaki2000design} as opposed to the long established motion
capture methods \cite{dasgupta1999making}.

\section{Technical Approach}

We now present our approach to autonomous construction of simple machines, particularly a
lever-fulcrum assembly to overturn heavy obstacles, in four major categories: (1) autonomous design,
(2) visual perception, (3) posture control, and (4) motion planning.

In any design, components have to be placed to satisfy a set of physical or domain constraints. For
instance, a candidate 2-by-4 block needs to make contact both with the load and the fulcrum,
essentially distance functions between objects, to satisfy physical constraints of the design.
However, for a design to be useful, we also impose that the contact point for the lever is further
away from the fulcrum than the load such that a mechanical advantage is achieved. In previous work,
we propose a nonlinear optimization approach where such geometric and dynamic constraints are
expressed as equality and inequality functions whose common zero-crossings are design configurations
that satisfy all the constraints. For this work, we use the planner to output the lever and the
fulcrum configurations, and the required contact point, but allow the robot to choose its closest
configuration, assuming it can supply the necessary force.

In perceiving the environment, we propose using a light-weight feature-based recognition approach as
opposed to full 3D based approaches that use the entire mesh data such as the iterative closest
point algorithm or over-segmentation methods. The key assumption of the work is that the planner
already knows the mesh of the available objects and with minimal additional feature knowledge, such
as the top of a cinder block is at 44 cm from the ground or a lever is at least 2 meters in one
dimension, we can speed up detection. At its current stage, the agent can autonomously detect cinder
blocks, the load as shown in Figure 1, the walls and the 2-by-4 levers. To localize objects of
interest, we perform a simple scan with the tilt and pan degrees of freedom of the RGBD camera,
taking also into account the robot kinematics. Figure \ref{fig:detection} demonstrates the detection module.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/detection.png}
  \caption{The mechanical advantage in forces}
  \label{fig:detection}
\end{figure}

For the locomotion controllers, we model Krang as a simple inverse pendulum and use a
proportional-derivative control with gain scheduling for different robot poses to minimize the
frequency of oscillations in dynamic balancing. In picking up cinder blocks, the torque around the
wheel axis due to the additional force at the end-effector is incorporated in computing the goal
balancing angle.

Lastly, for motion planning, we use a variety of approaches. First, to grasp objects, we use
analytical inverse kinematics to determine if there is a configuration close to the object we can
reach without collisions. Once close, we perform Jacobian inverse kinematics to approach the object
and detect contact with the object with the gripper force-torque sensor. Analytical inverse
kinematics is used as a resolution-complete method to determine whether a collision-free grasp
configuration exists as opposed to sampling the large configuration space of the arms to avoid local
minima with Jacobian.s In addition to motion planning for the arms, we also make use of an example
of conformant planning in picking up a lever. The motivation is to avoid perception problems by
running each wheel to the 2-by-4 on the ground while the wheels cannot exert the torque to climb
over the object. Thus, the robot autonomously aligns itself with the object of interest by using
contact points without the need for precise perception.

\section{Results}

Our results demonstrate Golem Krang autonomously construct a simple machine design, specifically a
lever-fulcrum assembly, and use it to overturn a 45 kg load. To achieve such an autonomous behavior,
we propose a set of modules that accomplish object detection and localization, balancing and
navigation controller in the presence of external disturbances, and a rich set of motion planning
modules. To demonstrate the execution of the task, we designed the following scenario (see
\url{http://tinyurl.com/mw2ehxl} for video):

We position Golem Krang in the middle of the room and instruct it to use the closest cinder block as
a fulcrum. Using the aforementioned tools, the robot picks up the object (e.g. reacts to its weight
by leaning backwards) and carries it to the predetermined position instructed by the constraint
optimization planner. During locomotion, we assume that there are no obstacles on the path of the
robot, and the robot uses the turn-forward-turn tactic to move between two planar poses. Once the
robot places the fulcrum, it scans its surroundings for a lever and once located, approaches it
using the perception data. To minimize the effect of perception errors, once within 0.5 meters of
the lever, the robot deploys the wheel contact approach to position itself exactly in front of the
object and takes it back to the load. Finally, the robot positions the lever with Jacobian control
and exerts force with the top joint in its 7-dof arm.

\section{Experiments}

A significant challenge in accomplishing the series of the autonomous manipulation and perception
tasks has been the accumulation of error over the course of the executions. To remedy such an error
build-up, at the current state of our work, the authors intervene and instruct the robot to minimize
its position errors. We focus on the two main reasons and propose possible solutions.

During experiments, we observed that the RGBD data becomes more erroneous as the distance increases.
Within a 1 meter bound, the mean error is within 2-3 cm whereas with the maximum 4 meters (e.g. the
room limits), we see errors up to 10 cm. The proportional increase of error with respect to distance
suggest a camera calibration problem. Another source of error could be the slack in the tilt and pan
joints that control the camera view. The general of camera calibration has been addressed via bundle
adjustment in [2].

A second reason we suspect that might lead to localization errors is the error accumulated while the
robot attempts to follow a velocity profile in the forward direction. Figure \ref{fig:controller} demonstrates the
reference position and velocity trajectories (green), along with the real trajectories (red). To
remedy this error, we will focus on the trajectory following techniques developed by [7].

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.6\linewidth]{Figures/controller.png}
  \caption{The mechanical advantage in forces}
  \label{fig:controller}
\end{figure}

Lastly, the main experiment of our work is the successful overturning of the 45 kg obstacle. Figure
4 demonstrate the forces measured at the robot gripper as it pushes the lever until the obstacle
falls. Given that the load is approximately 500N and the maximum force is 250N, we observe an
advantage of 2:1.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.6\linewidth]{Figures/plot.png}
  \caption{The mechanical advantage in forces}
  \label{fig:plot}
\end{figure}

\section{Experimental Insights}

We offer two insights from our experiments. First, the manipulation of heavy objects brings about
interesting challenges. If the object inertia model is not known, the system can be thrown off
balance easily. Moreover, when the mass of the object is mostly on one of the wheels, the robot can
start spinning since one wheel has to accommodate the extra weight. Second, the constraint
optimization planner outputs too precise (e.g. 1$e^{-5}$) configurations which we observe clearly
cannot be executed to the same level of precision. We propose extending the planner for iterative
solutions and/or soft constraints.

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2014-05-26 doc/paper/paper.tex
exp first figure done

@@
 kg 2-by-4 block blocks (e.g. potential levers), relocates them to the desired configurations output
-by the constraint planner, and actuates them to flip a 45 kg load. Figure \ref{fig:showOff} demonstrates key scenes
+by the constraint planner, and actuates them to flip a 50 kg load. Figure \ref{fig:showOff} demonstrates key scenes
 from this scenario such as (a) detection of a cinder block, (b) locomotion with a heavy load, (c)
@@
 
-Golem Krang is tasked with overturning a 45 kg load using a lever-fulcrum assembly with a limit of
-\textcolor{red}{TBA} Nm on the force it can apply to the environment. Given the dimensions of the 
+Golem Krang is tasked with overturning a 50 kg load using a lever-fulcrum assembly with a limit of
+300 Nm on the force it can apply to the environment. Given the dimensions of the 
 available objects in the environment, the robot has to design a structure, locate the components,
@@
 such an artifact, in Figure \ref{fig:typical_b}, Golem Krang first moves the grasped cinder block 
-to the middle of its torso before turning around and localizing the load object at 45 kg. Having
+to the middle of its torso before turning around and localizing the load object at 50 kg. Having
 detected the load, the final configuration of the fulcrum is deduced from the assembly design and
@@
   \includegraphics[width=1.0\linewidth]{Figures/d.png}
-  \caption{The mechanical advantage in forces}
+  \caption{Golem Krang places the lever in the planned pose and overturns the 50 kg load.}
   \label{fig:typical_d}
@@
 
-\subsection{Designs with Different Load Weights and Lever Choices}
+\subsection{Designs with Different Load Weights}
+
+To assess the ability of the proposed design algorithm, the framework is tested with two different
+load sizes, 50 kg and 100 kg, where the planner needs to choose from two different levers 1.7 and 2.5
+m long in each case. Once a choice is made, Golem Krang autonomously constructs the design, as
+described in Section 3, and we measure the force/torque sensor readings at the end-effector of
+the actuating arm. Figure \ref{fig:comparison} demonstrates the readings for the two experiments
+where the maximum applied forces are 242.27 Nm and 368.63 Nm for 50 kg and 100 kg experiments
+respectively. We conclude that the mechanical advantage is 2.02:1 and 2.66:1 for each case, and 
+the maximum force limit is preserved; and thus, the planned design, its assembly and actuation are
+successful.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=0.7\linewidth]{Figures/loads.png}
+  \caption{The mechanical advantage in forces}
+  \label{fig:comparison}
+\end{figure}
+
+\subsection{Fulcrum Base Choice and Unmodeled Implications}
 

### 2014-05-26 data/experiments/09-push/fuck.m

@@ -1,0 +1,9 @@
+load fts;
+load fts2;
+clf;
+xx = []; for i = 1 : 600, xx(end+1) = norm(fts(i,:)); end;
+xx2 = []; for i = 4500 : size(fts2,1) - 430, xx2(end+1) = norm(fts2(i,:)); end;
+plot(-xx, 'r', 'LineWidth', 12); hold on;
+plot(-xx2, 'g', 'LineWidth', 12);
+axis([0 600 -400 50]); 
+set(gca,'FontSize',35);

### 2014-05-26 doc/paper/paper.tex
exps halfway done

@@
 
-\subsection{Designs with Different Load Weights}
+\subsubsection{Designs with Different Load Weights}
 
-To assess the ability of the proposed design algorithm, the framework is tested with two different
-load sizes, 50 kg and 100 kg, where the planner needs to choose from two different levers 1.7 and 2.5
-m long in each case. Once a choice is made, Golem Krang autonomously constructs the design, as
-described in Section 3, and we measure the force/torque sensor readings at the end-effector of
-the actuating arm. Figure \ref{fig:comparison} demonstrates the readings for the two experiments
-where the maximum applied forces are 242.27 Nm and 368.63 Nm for 50 kg and 100 kg experiments
+The proposed framework is tested with two 
+load sizes, 50 kg and 100 kg, where the planner chooses from two levers 1.7 and 2.5
+m long. Once the design is made, Golem Krang autonomously constructs it, as
+described in Section 3, and we measure the force/torque sensor readings at the actuating arm gripper.
+Figure \ref{fig:graphs}a demonstrates the maximum applied forces at 242.27 Nm and 368.63 Nm for 50 kg and 100 kg experiments
 respectively. We conclude that the mechanical advantage is 2.02:1 and 2.66:1 for each case, and 
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{Figures/loads.png}
-  \caption{The mechanical advantage in forces}
-  \label{fig:comparison}
+  \includegraphics[width=1.0\linewidth]{Figures/loads.png}
+  \caption{Left: Input forces during the 50 kg (red) and 100 kg (red) overturning tasks. 
+  Right: Fulcrum shift while using a small lever leads to increased input force  (grey line).}
+
+  \label{fig:graphs}
 \end{figure}
 
-\subsection{Fulcrum Base Choice and Unmodeled Implications}
+\vspace{-2em}
+\subsubsection{Fulcrum Base Choice and Unmodeled Implications}
+
+The proposed planner focuses on the initial moment of force application and ensures that the force
+induces enough torque to overturn the load. Although constraints are used to guarantee that the
+motion is collision-free, the possibility of the the contact between
+the lever and the cinder block moving is not considered. Figure \ref{fig:short}a demonstrates a case where
+the planner \textit{autonomously} adapts the fulcrum base choice to accommodate the short
+lever. However, the fulcrum point moves (Figures \ref{fig:short}b-c) because the contact height is
+shorter than the center of mass of the load. Figure \ref{fig:graphs}b displays the increase in
+the required force as the fulcrum shifts.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=1.0\linewidth]{Figures/short.png}
+  \caption{.}
+  \label{fig:short}
+\end{figure}
+
+\subsubsection{Evaluating Accuracy}
+
+DONT READ HERE YET!
+
+A significant challenge in accomplishing the series of the autonomous manipulation and perception
+tasks has been the accumulation of error over the course of the executions. To remedy such an error
+build-up, at the current state of our work, the authors intervene and instruct the robot to minimize
+its position errors. We focus on the two main reasons and propose possible solutions.
+
+During experiments, we observed that the RGBD data becomes more erroneous as the distance increases.
+Within a 1 meter bound, the mean error is within 2-3 cm whereas with the maximum 4 meters (e.g. the
+room limits), we see errors up to 10 cm. The proportional increase of error with respect to distance
+suggest a camera calibration problem. Another source of error could be the slack in the tilt and pan
+joints that control the camera view. The general of camera calibration has been addressed via bundle
+adjustment in \cite{dasgupta1999making}.
+
+A second reason we suspect that might lead to localization errors is the error accumulated while the
+robot attempts to follow a velocity profile in the forward direction. Figure \ref{fig:controller} demonstrates the
+reference position and velocity trajectories (green), along with the real trajectories (red). To
+remedy this error, we will focus on the trajectory following techniques developed by \cite{ha1996trajectory}.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=0.6\linewidth]{Figures/controller.png}
+  \caption{The mechanical advantage in forces}
+  \label{fig:controller}
+\end{figure}
 

### 2014-05-26 doc/paper/paper.tex
1/4 left in results

@@
 
-DONT READ HERE YET!
+A challenge in long-term manipulation tasks is the accumulation of error over the course of the
+executions. To remedy such an error build-up, at the current state of our work, the authors
+intervene and instruct the robot to minimize its error if necessary. One of the main causes of this
+inaccuracy is the reliability of the RGBD data. We observe that a mean error of 2-3 cm within a 1 m
+bound increases up to 10 cm with 4 meters. The proportional increase in error with respect to
+distance suggest a camera calibration problem which can be addressed with bundle adjustment \cite{dasgupta1999making}.
 
-A significant challenge in accomplishing the series of the autonomous manipulation and perception
-tasks has been the accumulation of error over the course of the executions. To remedy such an error
-build-up, at the current state of our work, the authors intervene and instruct the robot to minimize
-its position errors. We focus on the two main reasons and propose possible solutions.
-
-During experiments, we observed that the RGBD data becomes more erroneous as the distance increases.
-Within a 1 meter bound, the mean error is within 2-3 cm whereas with the maximum 4 meters (e.g. the
-room limits), we see errors up to 10 cm. The proportional increase of error with respect to distance
-suggest a camera calibration problem. Another source of error could be the slack in the tilt and pan
-joints that control the camera view. The general of camera calibration has been addressed via bundle
-adjustment in \cite{dasgupta1999making}.
-
-A second reason we suspect that might lead to localization errors is the error accumulated while the
-robot attempts to follow a velocity profile in the forward direction. Figure \ref{fig:controller} demonstrates the
-reference position and velocity trajectories (green), along with the real trajectories (red). To
-remedy this error, we will focus on the trajectory following techniques developed by \cite{ha1996trajectory}.
+Secondly, locomotion for heavy balancing robots is an active research area and our implementation
+with a proportional-derivative controller can be improved following techniques as presented in
+\cite{ha1996trajectory}. A major challenge is the system modeling, specifically accurate center of
+mass and inertia information. Figure \ref{fig:controller} demonstrates the behavior of the robot as
+it follows a velocity profile, moving straight. The sinusoidal behavior in the output position
+trajectory (red) is the robot regaining its balance and the steady state error may be accommodated
+with an integral term in the controller. A concern is the high-frequency velocity sinusoids which may cause instability when heavy objects are manipulated.
 
@@
   \centering
-  \includegraphics[width=0.6\linewidth]{Figures/controller.png}
+  \includegraphics[width=0.9\linewidth]{Figures/controller.png}
   \caption{The mechanical advantage in forces}
@@
 \end{figure}
+
+\subsection{}
 

### 2014-05-26 doc/paper/paper.tex
did the references. still need to finish results

@@
 bound increases up to 10 cm with 4 meters. The proportional increase in error with respect to
-distance suggest a camera calibration problem which can be addressed with bundle adjustment \cite{dasgupta1999making}.
+distance suggest a camera calibration problem which can be addressed with bundle adjustment \cite{pradeep2014calibrating}.
 
@@
   \includegraphics[width=0.9\linewidth]{Figures/controller.png}
-  \caption{The mechanical advantage in forces}
+  \caption{The oscillations and steady state error in following a reference velocity profile.}
   \label{fig:controller}
@@
 
-\subsection{}
+\subsubsection{Manipulation of Heavy Objects}
+
+We offer two insights from our experiments. First, the manipulation of heavy objects brings about
+interesting challenges. If the object inertia model is not known, the system can be thrown off
+balance easily. Moreover, when the mass of the object is mostly on one of the wheels, the robot can
+start spinning since one wheel has to accommodate the extra weight.
 
 \newpage
-\bibliographystyle{plain}
-\bibliography{references}
+% \bibliographystyle{unsrt}
+% \bibliography{references}
+
+\begin{thebibliography}{27}
+
+\bibitem{erdogan2013planning} Erdogan, C., Stilman, M: Planning in constraint space: Automated design of
+functional structures. ICRA, 2013.
+\bibitem{erdogan2014incorporating} Erdogan, C., Stilman, M: Incorporating kinodynamic constraints in automated
+design of simple machines. IROS, 2014.
+\bibitem{vidal2006branching} Vincent, V., Geffner, H.: Branching and pruning: An optimal temporal pocl planner
+based on constraint programming. AI, 2006.
+\bibitem{yu2011make} Yu, L. F., Yeung, S. K., Tang, C. K., Terzopoulos, D., Chan, T. F., Osher, S: Make it home:
+automatic optim. of furniture arrangement. In Siggraph, 2011.
+\bibitem{beetz2010cram} Beetz, M., Mosenlechner, L., Tenorth, M: Crama cognitive robot
+abstract machine for everyday manipulation in human environments. In IROS,
+2010.
+\bibitem{stilman2005navigation} Stilman, M., Kuffner, J. J.: Navigation among movable obstacles: Real-
+time reasoning in complex environments. IJHR, 2005.
+\bibitem{kemp2007challenges} Kemp, C. C., Edsinger, A., Torres-Jara, E: Challenges for robot
+manipulation in human environments. IEEE Robotics and Automation Magazine,
+14(1):20, 2007.
+\bibitem{kuindersma2009dexterous} Kuindersma, S. R., Hannigan, E., Ruiken, D., and Grupen, R. A:
+Dexterous mobility with the ubot-5 mobile manipulator. ICAR, 2009.
+\bibitem{srinivasa2010herb}  Srinivasa, S. S., Ferguson, D., Helfrich, C. J., Berenson, D., 
+Collet, A., Diankov, R., Gallagher, R., Hollinger, G., Kuffner, J., and
+Weghe, M. V.. Herb: a home exploring robotic butler. Autonomous Robots,
+28(1):5–20, 2010.
+\bibitem{nishiwaki2000design} Nishiwaki, K., Sugihara, T., Kagami, S., Kanehiro, F.,
+Inaba, M., and Inoue, H.: Design and development of research platform for perception-action 
+integration in humanoid robot: H6. IROS, 2000.
+\bibitem{dasgupta1999making} Dasgupta, A., Nakamura, Y.: Making feasible walking motion of
+humanoid robots from human motion capture data. ICRA, 1999.
+\bibitem{yamauchi2004packbot} Yamauchi, M. B.: Packbot: a versatile platform for military robotics. In Defense
+and Security, pages 228–237. International Society for Optics and Photonics, 2004.
+\bibitem{saranli2001rhex} Saranli, U., Buehler, M., Koditschek, D. E.. Rhex: A simple and
+highly mobile hexapod robot. IJRR, 2001.
+\bibitem{newell1961gps} Newell, A., Simon, H.: GPS, a program that simulates human thought.
+DTIC, '61.
+\bibitem{mccarthy1963programs} McCarthy, J.: Programs with common sense. DTIC, 1963.
+\bibitem{fulkerson1961network} Fulkerson, D. R.: A network flow computation for project cost curves. Management science, 7(2):167–178, 1961.
+\bibitem{taha1975integer} Taha, H.A.: Integer programming: theory, applications, and computations,
+volume 975. Academic Press New York, 1975.
+\bibitem{fikes1972strips} Fikes, R. E., Nilsson, N. J.: Strips: A new approach to the application of
+theorem proving to problem solving. Artificial intelligence, 2(3):189–208, 1972.
+\bibitem{stilman2010golem} Stilman, M., Olson, J., Gloss, W.: Golem krang: Dynamically stable
+humanoid robot for mobile manipulation. ICRA, 2010.
+\bibitem{kuffner2000rrt} Kuffner J.J., LaValle, S.M.: RRT-connect: An efficient approach to single-
+query path planning. In ICRA. IEEE, 2000.
+\bibitem{tolani2000real} Tolani, D., Goswami, A., Badler, N. I.: Real-time inverse kinematics techniques for anthropomorphic limbs. Graphical models, 62(5):353–388,
+2000.
+\bibitem{whitney1969resolved} Whitney, D. E.: Resolved motion rate control of manipulators and human pros-
+theses. IEEE Transactions on man-machine systems, 1969.
+\bibitem{bejczy1977effect} Bejczy, A.K.: Effect of hand-based sensors on manipulator control performance.
+Mechanism and Machine Theory, 12(5):547–567, 1977.
+\bibitem{goldman1996expressive} Goldman, R., Boddy, M.: Expressive planning and explicit knowledge. AIPS, 1996.
+\bibitem{mason1986mechanics} Mason, M.T.: Mechanics and planning of manipulator pushing operations.
+The International Journal of Robotics Research, 5(3):53–71, 1986.
+\bibitem{pradeep2014calibrating} Pradeep, V., Konolige, K., Berger, E.: Calibrating a multi-arm multi-
+sensor robot: A bundle adjustment approach. In Experimental Robotics, 1999.
+\bibitem{ha1996trajectory} Ha, Y., Yuta, S.: Trajectory tracking control for navigation of the
+inverse pendulum type self-contained mobile robot. Robotics and autonomous systems, 1996.
+
+\end{thebibliography}
 

### 2014-05-27 doc/paper/paper.tex
shrinked images to save file sizes and 'finished' results. next: clean up the paper to make room for discussion

@@
 
-\newpage
 \section{Technical Approach}
@@
 
-\vspace{-2em}
 \subsubsection{Guarded and conformant motions}
@@
   \includegraphics[width=1.0\linewidth]{Figures/short.png}
-  \caption{.}
+  \caption{The movement of the fulcrum-lever contact point for short lever objects.}
   \label{fig:short}
@@
 
-We offer two insights from our experiments. First, the manipulation of heavy objects brings about
-interesting challenges. If the object inertia model is not known, the system can be thrown off
-balance easily. Moreover, when the mass of the object is mostly on one of the wheels, the robot can
-start spinning since one wheel has to accommodate the extra weight.
+The manipulation of heavy objects brings about interesting challenging in manipulation, locomotion
+and control fields. First of all, even though the mass and the center of mass information of a
+carried load is sufficient in maintaining quasi-static balance, the inertias are needed when
+the motion become faster. Although most of the time, the dynamic parameters of manipulated objects
+is not readily available, there are a variety of methods to estimate them with simple experiments
+\cite{saal2010active} or with simplifying assumptions based on geometry and mass.
 
-\newpage
-% \bibliographystyle{unsrt}
-% \bibliography{references}
+Secondly, we observe that the configuration of the grasped object with respect to the body frame
+can affect the accuracy of locomotion. For instance, carrying a 15 kg load in the middle of the 
+two wheels as opposed to a meter off to the side induces different output trajectories for the 
+same velocity profiles. Figure \ref{fig:wheels} demonstrates the effect of the distribution 
+of the load mass over the wheels where the robot moves a cinder block from +1 meter to the -1 meter off
+its center and attempts to follow a straight line. The results show a proportional relationship
+where the trajectories bias towards the load increases with the distance between the load and the center. 
+We speculate that the cause is that the wheel with the more weight on has to apply more torque
+to keep up with the other one. Note that the distribution of the load and its effect of the joint
+torques is a general issue that also affects legged humanoid robots.
+
+\begin{figure}[ht!] 
+  \centering
+  \includegraphics[width=0.9\linewidth]{Figures/wheels.png}
+  \caption{The effect of the grasping location on the accuracy of locomotion.}
+  \label{fig:wheels}
+\end{figure}
+
+Lastly, the mass and the sheer size of the manipulated objects can cause problems with robust
+grasping during locomotion. For instance, for Golem Krang's grippers with two prismatic finger joints,
+it is important to guarantee that an object would not slip from its grasp as the robot turns around
+swiftly. To handle such cases, we have adopted a two-hand grasp for the cinder block and ensured
+that the lever is held mostly from its middle region and at an upwards angle.
+
+\section{Discussion}
 
@@
 inverse pendulum type self-contained mobile robot. Robotics and autonomous systems, 1996.
-
+\bibitem{saal2010active} Saal, H. P., Ting, J. A.,  Vijayakumar, S.: Active estimation of object dynamics
+parameters with tactile sensors. IROS, 2010. 
 \end{thebibliography}
@@
 % DISCUSSION: CHALLENGES WITH VISUAL SERVOING A NONHOLONOMIC ROBOT BASE
+% Lastly, we observe that the manipulation of multiple objects to assemble functional structures
+% is closely related to the grasp problem where the manipulator has to choose how to grasp the objects.
+% In this work, we use predetermined grasp areas for the cinder block and the planner is provided
+% the orientation of the hand as the robot grasps the lever. Moreover, learning from the effect
+% of the carried load configuration on locomotion, we adopt an atomic behavior that holds the load
+% in the middle of the robot.
 

### 2014-05-27 doc/bias_exps/bla.m

@@ -1,0 +1,46 @@
+clf;
+load exp1;
+load exp2;
+load exp3;
+load exp4;
+load exp5;
+load exp6;
+load exp7;
+load exp8;
+load exp9;
+k = 1000;
+lw = 7;
+ms = 20;
+subplot(2,1,1);
+plot(exp5(1:k:end,1), exp5(1:k:end,3), "-xm", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot(exp4(1:k:end,1), exp4(1:k:end,3), "-xc", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot(exp3(1:k:end,1), exp3(1:k:end,3), "-xg", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot(exp2(1:k:(size(exp2,1)-k),1), -exp2(1:k:(size(exp2,1)-k),3), "-xr", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot(exp8(1:k:end,1), exp8(1:k:end,3), "o--c", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot(exp9(1:k:end,1), exp9(1:k:end,3), "o--m", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot(exp7(1:k:end,1), exp7(1:k:end,3), "o--g", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot(exp6(1:k:end,1), exp6(1:k:end,3), "o--r", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot(exp1(1:k:end,1), exp1(1:k:end,3), "-^", 'LineWidth', lw, 'MarkerSize', ms); hold on;  
+
+plot([0.25]-1.5, [-3.5]+0.8, "ro", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot([0.25]-1.5, [-3.5]+0.2, "go", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot([0.25]-1.5, [-3.5]-0.4, "co", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
+plot([0.25]-1.5, [-3.5]-1.0, "mo", 'LineWidth', lw, 'MarkerSize', ms); hold on; 
[…]
